---
title: "DPNR Outplant Analyses"
format:
  html:
    theme: cosmo
    toc: true
    code-fold: true
    embed-resources: true
execute:
  echo: true
  warning: false
  message: false
---

## Select the Plot that you would like to view

::: panel-tabset
## Home

This report analyzes DPNR coral outplant monitoring data from TagLab match files. The workflow is designed for repeated use: add new plot/month files to the config, render the report, and the tables and figures rebuild automatically.

The current test case is Plot E, chunk 1-1, using same-batch TagLab match exports from May through November. The analysis tracks outplant survivorship, interval survival, coral cover, species prevalence, species cover composition, temperature, and plot-level depth metadata.

The two recommended datasets to open first are:

-   `data_processed/outplant_master_tracking_dataset.csv`: one row per tracked `Genet` per month, including presence, area, cover contribution, and baseline-survival status.
-   `outputs/Tables/outplant_master_summary_dataset.csv`: one long-format summary table containing cumulative survivorship, interval survivorship, coral cover, species prevalence, and species cover-share metrics.

Each plot tab is organized with the same outline so new data can be added without redesigning the report: overview, data status, depth metadata, QA/QC, cumulative survivorship, interval survivorship, coral cover, species prevalence, species cover composition, and downloads.

## SOP

1.  Export TagLab match files for each plot/month pair using the same batch export process so `Genet` IDs stay consistent across months.
2.  Place the exported CSV files in `data_raw/taglab/<Plot_Folder>/`.
3.  Add one row per month-to-month match file in `config/outplant_interval_files.csv`.
4.  Confirm each config row has the correct plot name, plot folder, filename, start month, end month, file type, plot dimensions, and TagLab area units.
5.  Confirm `data_raw/metadata/Coordinates_Depths.csv` has marker depths for each plot if depth summaries will be used.
6.  Render this Quarto report.
7.  Check the file audit and QA/QC tables first.
8.  Confirm the shared-month continuity table has zero missing Genets, zero unexpected new Genets, and zero species mismatches.
9.  Use cumulative survivorship as the main survival result.
10. Use interval survivorship as a diagnostic for each month-to-month transition.
11. Open the two master datasets when exporting or sharing results.

## Main Work Flow

This setup chunk loads the packages needed for table formatting and data manipulation, then sources the outplant interval workflow. Sourcing the script here means the report always rebuilds from the latest raw/config files when rendered.

```{r}
#| label: setup
#| message: false
#| warning: false

library(tidyverse)
library(knitr)

# Find the project folder from the report location. This lets collaborators move
# the full project folder anywhere on their computer and still render the report.
report_path <- knitr::current_input(dir = TRUE)
report_dir <- if (!is.null(report_path)) {
  dirname(normalizePath(report_path, mustWork = TRUE))
} else {
  getwd()
}

project_root <- report_dir
while (!file.exists(file.path(project_root, "config", "outplant_interval_files.csv"))) {
  parent_dir <- dirname(project_root)
  if (identical(parent_dir, project_root)) {
    stop(
      "Could not find config/outplant_interval_files.csv. ",
      "Render this report from inside the Coral_survivorship_project folder.",
      call. = FALSE
    )
  }
  project_root <- parent_dir
}

knitr::opts_knit$set(root.dir = project_root)
setwd(project_root)

source(file.path(project_root, "R", "03_outplant_interval_workflow.R"))
```

### Workflow

This report reads the outplant-only TagLab match files listed in `config/outplant_interval_files.csv`, standardizes them into common start/end area columns, collapses repeated blob rows to one tracked `Genet` per interval, and produces survivorship, cover, and species-composition outputs.

The workflow is designed so future users can add new plots or month pairs by editing the config rather than changing analysis code.

The two recommended outplant datasets to open first are:

-   `data_processed/outplant_master_tracking_dataset.csv`: one row per tracked `Genet` per month, including presence, area, cover contribution, and baseline-survival status.
-   `outputs/Tables/outplant_master_summary_dataset.csv`: one long-format summary table containing cumulative survivorship, interval survivorship, coral cover, species prevalence, and species cover-share metrics.

The workflow still writes detailed intermediate CSVs for QA/QC and reproducibility, but most users should only need the two files above unless they are debugging the analysis.

Survivorship is treated as apparent persistence through a TagLab interval: an outplant is counted as surviving when it has measurable area at the start and end of the interval.

### Outplant-Only Plot E Workflow

This is the main test workflow for the outplant-only TagLab match files. It treats `Area1` as the start-month area and `Area2` as the end-month area, and calculates cover using the configured 16 by 30 m plot area. The same-batch TagLab exports use `Genet` as the across-month tracking ID. If a `Genet` has multiple blob rows in one interval, those rows are collapsed into one tracked outplant before survivorship is calculated. The area unit is read from `config/outplant_interval_files.csv`; the current test assumes TagLab areas are in square centimeters.

This chunk verifies that every outplant interval file listed in the config exists. This is the first place to check when adding new files for other plots or months.

```{r}
#| label: outplant-file-audit

outplant_file_audit %>%
  select(plot, month_start, month_end, match_type, file, file_exists) %>%
  kable(
    col.names = c("Plot", "Start month", "End month", "Match type", "File", "File exists")
  )
```

This chunk checks whether the TagLab files have missing `Genet` IDs, missing species, negative areas, or unusual action/split-fuse labels. These checks catch export problems before the biological summaries are interpreted.

```{r}
#| label: outplant-interval-qa

outplant_interval_qa %>%
  select(
    month_start,
    month_end,
    n_rows,
    n_missing_genet,
    n_missing_species,
    n_negative_area_start,
    n_negative_area_end,
    actions,
    split_fuse_events
  ) %>%
  kable(
    col.names = c(
      "Start month", "End month", "Rows", "Missing Genet", "Missing species",
      "Negative start area", "Negative end area", "Actions", "Split/fuse events"
    )
  )
```

This chunk checks whether the same `Genet` number maps to different species, tags, or genotypes across files. If the table says no conflicts were detected, the same-batch export is behaving much better for individual-level survivorship.

```{r}
#| label: outplant-unstable-genet-examples

if (nrow(outplant_unstable_genet_examples) == 0) {
  tibble(status = "No cross-file Genet identity conflicts detected.") %>%
    kable(col.names = "Status")
} else {
  outplant_unstable_genet_examples %>%
    slice_head(n = 20) %>%
    kable(
      col.names = c(
        "Plot", "Source file", "Start month", "End month", "Genet",
        "Tag", "Genotype", "Species", "Action", "Start area", "End area"
      )
    )
}
```

This chunk checks whether the same shared month matches between adjacent files after repeated `Genet` blob rows have been collapsed. A good export should have zero missing/new Genets and zero species mismatches for each shared month. Area mismatches can occur when TagLab split/fuse behavior changes how multiple blobs are grouped under the same `Genet`.

```{r}
#| label: outplant-shared-month-continuity

outplant_shared_month_continuity_qa %>%
  select(
    shared_month,
    previous_end_n,
    next_start_n,
    in_both_snapshots,
    missing_from_next_start,
    new_in_next_start,
    species_mismatches,
    area_mismatches,
    max_abs_area_difference
  ) %>%
  mutate(max_abs_area_difference = round(max_abs_area_difference, 4)) %>%
  kable(
    col.names = c(
      "Shared month", "Previous file end n", "Next file start n",
      "In both", "Missing from next start", "New in next start",
      "Species mismatches", "Area mismatches", "Max area difference"
    )
  )
```

This chunk summarizes cumulative outplant survivorship from the baseline month. May is treated as 100%, and later months report how many original May `Genet` IDs are still present.

```{r}
#| label: outplant-cumulative-survival-table

outplant_cumulative_survival_summary %>%
  select(
    month,
    baseline_month,
    n_baseline,
    n_died_interval,
    cumulative_deaths_observed,
    n_surviving_from_baseline,
    percent_cumulative_survival,
    percent_cumulative_survival_low,
    percent_cumulative_survival_high
  ) %>%
  mutate(
    percent_cumulative_survival = round(percent_cumulative_survival, 1),
    percent_cumulative_survival_low = round(percent_cumulative_survival_low, 1),
    percent_cumulative_survival_high = round(percent_cumulative_survival_high, 1)
  ) %>%
  kable(
    col.names = c(
      "Month", "Baseline month", "Baseline n", "Deaths this interval",
      "Cumulative deaths", "Surviving from baseline",
      "Cumulative survival (%)", "95% CI low", "95% CI high"
    )
  )
```

This chunk summarizes the Deep Nursery temperature logger data used in the cumulative survivorship figure. The logger is slightly deeper than the outplant site but close enough for this practice overlay.

```{r}
#| label: outplant-temperature-summary

outplant_daily_temperature_summary %>%
  summarise(
    logger_location = first(logger_location),
    start_date = min(date),
    end_date = max(date),
    n_days = n(),
    mean_temperature_c = mean(mean_temperature_c, na.rm = TRUE),
    min_temperature_c = min(min_temperature_c, na.rm = TRUE),
    max_temperature_c = max(max_temperature_c, na.rm = TRUE)
  ) %>%
  mutate(
    mean_temperature_c = round(mean_temperature_c, 2),
    min_temperature_c = round(min_temperature_c, 2),
    max_temperature_c = round(max_temperature_c, 2)
  ) %>%
  kable(
    col.names = c(
      "Logger", "Start date", "End date", "Days",
      "Mean temp (°C)", "Min temp (°C)", "Max temp (°C)"
    )
  )
```

This chunk plots cumulative outplant survivorship from the baseline month. The red line shows daily mean temperature on the secondary y-axis.

```{r}
#| label: outplant-cumulative-survival-plot
#| fig-width: 9
#| fig-height: 4.8

outplant_cumulative_survival_plot
```

This chunk reports interval survivorship between adjacent survey months. It is useful as a diagnostic because a later interval can be 100% even if cumulative survivorship has already declined.

```{r}
#| label: outplant-interval-survival-table

outplant_survival_summary %>%
  select(
    interval_label,
    n_start,
    n_survived,
    n_died,
    n_born,
    percent_survival,
    percent_survival_low,
    percent_survival_high
  ) %>%
  mutate(
    percent_survival = round(percent_survival, 1),
    percent_survival_low = round(percent_survival_low, 1),
    percent_survival_high = round(percent_survival_high, 1)
  ) %>%
  kable(
    col.names = c(
      "Interval", "Start n", "Survived n", "Died n", "Born n",
      "Interval survival (%)", "95% CI low", "95% CI high"
    )
  )
```

This chunk plots interval survivorship between adjacent survey months. This is why October-to-November can be 100% even when cumulative survivorship is lower.

```{r}
#| label: outplant-interval-survival-plot
#| fig-width: 9
#| fig-height: 4.8

outplant_survival_plot
```

This chunk reports outplant coral cover by month. Cover is calculated as summed outplant area divided by the 480 m2 plot area.

```{r}
#| label: outplant-cover-table

outplant_cover_summary %>%
  select(month, n_outplants_present, total_outplant_area_m2, plot_area_m2, percent_outplant_cover) %>%
  mutate(
    total_outplant_area_m2 = round(total_outplant_area_m2, 6),
    percent_outplant_cover = round(percent_outplant_cover, 5)
  ) %>%
  kable(
    col.names = c(
      "Month", "Outplants present", "Total outplant area (m2)",
      "Plot area (m2)", "Outplant cover (%)"
    )
  )
```

This chunk plots outplant cover through time. Because outplants are small relative to a 480 m2 plot, the percent cover values are expected to be very small.

```{r}
#| label: outplant-cover-plot
#| fig-width: 8
#| fig-height: 4.8

outplant_cover_plot
```

This chunk summarizes species abundance and prevalence among present outplant annotations in each monthly snapshot. `n_outplants` is the abundance count, and `percent_prevalence` is that species' share of present outplants for that month.

```{r}
#| label: outplant-species-prevalence-table

outplant_species_prevalence_summary %>%
  select(
    month,
    species,
    n_outplants,
    percent_prevalence,
    total_outplant_area_m2,
    percent_cover_within_outplants
  ) %>%
  mutate(
    percent_prevalence = round(percent_prevalence, 1),
    total_outplant_area_m2 = round(total_outplant_area_m2, 6),
    percent_cover_within_outplants = round(percent_cover_within_outplants, 1)
  ) %>%
  kable(
    col.names = c(
      "Month", "Species", "Outplant abundance", "Prevalence (%)",
      "Outplant area (m2)", "Share of outplant cover (%)"
    )
  )
```

This chunk plots species prevalence through time using counts of present outplant annotations.

```{r}
#| label: outplant-species-prevalence-plot
#| fig-width: 8
#| fig-height: 4.8

outplant_species_prevalence_plot
```

This chunk plots each species' share of total outplant cover through time. It complements prevalence because a species can have fewer annotations but more cover.

```{r}
#| label: outplant-species-cover-plot
#| fig-width: 8
#| fig-height: 4.8

outplant_species_cover_plot
```

### Plot Depth Metadata

This chunk summarizes the corner-marker depth metadata for every plot listed in `data_raw/metadata/Coordinates_Depths.csv`. These values describe the plot-level depth context and should not be interpreted as exact depths for individual coral colonies.

```{r}
#| label: outplant-plot-depth-summary

outplant_plot_depth_summary %>%
  mutate(
    mean_depth_ft = round(mean_depth_ft, 1),
    min_depth_ft = round(min_depth_ft, 1),
    max_depth_ft = round(max_depth_ft, 1),
    depth_range_ft = round(depth_range_ft, 1),
    mean_depth_m = round(mean_depth_m, 2),
    min_depth_m = round(min_depth_m, 2),
    max_depth_m = round(max_depth_m, 2),
    depth_range_m = round(depth_range_m, 2),
    centroid_latitude = round(centroid_latitude, 6),
    centroid_longitude = round(centroid_longitude, 6)
  ) %>%
  kable(
    col.names = c(
      "Plot", "Depth markers", "Mean depth (ft)", "Min depth (ft)",
      "Max depth (ft)", "Depth range (ft)", "Mean depth (m)",
      "Min depth (m)", "Max depth (m)", "Depth range (m)",
      "Centroid latitude", "Centroid longitude"
    )
  )
```

This chunk joins the species prevalence results to the plot-level depth summary. It is a setup table for future species-depth analyses once multiple plots have outplant match files configured.

```{r}
#| label: outplant-species-depth-summary

outplant_species_depth_summary %>%
  select(
    plot,
    month,
    species,
    n_outplants,
    percent_prevalence,
    percent_cover_within_outplants,
    mean_depth_ft,
    min_depth_ft,
    max_depth_ft,
    depth_range_ft
  ) %>%
  mutate(
    percent_prevalence = round(percent_prevalence, 1),
    percent_cover_within_outplants = round(percent_cover_within_outplants, 1),
    mean_depth_ft = round(mean_depth_ft, 1),
    min_depth_ft = round(min_depth_ft, 1),
    max_depth_ft = round(max_depth_ft, 1),
    depth_range_ft = round(depth_range_ft, 1)
  ) %>%
  kable(
    col.names = c(
      "Plot", "Month", "Species", "Outplant abundance",
      "Prevalence (%)", "Share of outplant cover (%)", "Mean depth (ft)",
      "Min depth (ft)", "Max depth (ft)", "Depth range (ft)"
    )
  )
```

## Plot A

### Overview

Plot A is included as a placeholder for future outplant match-file analyses.

### Data Status

No Plot A outplant match files are currently configured. Add Plot A rows to `config/outplant_interval_files.csv`, then render this report to populate this tab through the same workflow.

### Depth Metadata

This section will show Plot A corner-marker depth summaries and plot-level depth-gradient context once Plot A outplant match files are configured.

### QA/QC

This section will summarize file checks, missing values, split/fuse labels, Genet consistency, and shared-month continuity once Plot A data are added.

### Cumulative Survivorship

This section will show the percentage of baseline Plot A outplants still present through time.

### Interval Survivorship

This section will show month-to-month Plot A survivorship between adjacent TagLab match files.

### Coral Cover

This section will show Plot A outplant cover through time using the configured plot area.

### Species Prevalence

This section will show Plot A outplant abundance and prevalence by species through time.

### Species Cover Composition

This section will show each species' share of total Plot A outplant cover through time.

### Downloads

This section will point to Plot A processed datasets, summary tables, and figures after Plot A data are configured.

## Plot B

### Overview

Plot B is included as a placeholder for future outplant match-file analyses.

### Data Status

No Plot B outplant match files are currently configured. Add Plot B rows to `config/outplant_interval_files.csv`, then render this report to populate this tab through the same workflow.

### Depth Metadata

This section will show Plot B corner-marker depth summaries and plot-level depth-gradient context once Plot B outplant match files are configured.

### QA/QC

This section will summarize file checks, missing values, split/fuse labels, Genet consistency, and shared-month continuity once Plot B data are added.

### Cumulative Survivorship

This section will show the percentage of baseline Plot B outplants still present through time.

### Interval Survivorship

This section will show month-to-month Plot B survivorship between adjacent TagLab match files.

### Coral Cover

This section will show Plot B outplant cover through time using the configured plot area.

### Species Prevalence

This section will show Plot B outplant abundance and prevalence by species through time.

### Species Cover Composition

This section will show each species' share of total Plot B outplant cover through time.

### Downloads

This section will point to Plot B processed datasets, summary tables, and figures after Plot B data are configured.

## Plot C

### Overview

Plot C is included as a placeholder for future outplant match-file analyses.

### Data Status

No Plot C outplant match files are currently configured. Add Plot C rows to `config/outplant_interval_files.csv`, then render this report to populate this tab through the same workflow.

### Depth Metadata

This section will show Plot C corner-marker depth summaries and plot-level depth-gradient context once Plot C outplant match files are configured.

### QA/QC

This section will summarize file checks, missing values, split/fuse labels, Genet consistency, and shared-month continuity once Plot C data are added.

### Cumulative Survivorship

This section will show the percentage of baseline Plot C outplants still present through time.

### Interval Survivorship

This section will show month-to-month Plot C survivorship between adjacent TagLab match files.

### Coral Cover

This section will show Plot C outplant cover through time using the configured plot area.

### Species Prevalence

This section will show Plot C outplant abundance and prevalence by species through time.

### Species Cover Composition

This section will show each species' share of total Plot C outplant cover through time.

### Downloads

This section will point to Plot C processed datasets, summary tables, and figures after Plot C data are configured.

## Plot D

### Overview

Plot D is included as a placeholder for future outplant match-file analyses.

### Data Status

No Plot D outplant match files are currently configured. Add Plot D rows to `config/outplant_interval_files.csv`, then render this report to populate this tab through the same workflow.

### Depth Metadata

This section will show Plot D corner-marker depth summaries and plot-level depth-gradient context once Plot D outplant match files are configured.

### QA/QC

This section will summarize file checks, missing values, split/fuse labels, Genet consistency, and shared-month continuity once Plot D data are added.

### Cumulative Survivorship

This section will show the percentage of baseline Plot D outplants still present through time.

### Interval Survivorship

This section will show month-to-month Plot D survivorship between adjacent TagLab match files.

### Coral Cover

This section will show Plot D outplant cover through time using the configured plot area.

### Species Prevalence

This section will show Plot D outplant abundance and prevalence by species through time.

### Species Cover Composition

This section will show each species' share of total Plot D outplant cover through time.

### Downloads

This section will point to Plot D processed datasets, summary tables, and figures after Plot D data are configured.

## Plot E

### Overview

Plot E is currently the configured test plot for the outplant-only TagLab match workflow.

### Data Status

The active Plot E files are:

```{r}
#| label: plot-e-configured-files

outplant_config %>%
  filter(plot == "Plot E") %>%
  select(plot, month_start, month_end, month_start_date, month_end_date, file, plot_length_m, plot_width_m, taglab_area_units) %>%
  kable(
    col.names = c(
      "Plot", "Start month", "End month", "Start date", "End date", "File",
      "Plot length (m)", "Plot width (m)", "Area units"
    )
  )
```

### Depth Metadata

The Plot E depth summary is based on the four corner markers in `data_raw/metadata/Coordinates_Depths.csv`. These depths describe the plot-level setting for the active outplant workflow.

```{r}
#| label: plot-e-depth-summary

outplant_plot_depth_summary %>%
  filter(plot == "Plot E") %>%
  mutate(
    mean_depth_ft = round(mean_depth_ft, 1),
    min_depth_ft = round(min_depth_ft, 1),
    max_depth_ft = round(max_depth_ft, 1),
    depth_range_ft = round(depth_range_ft, 1),
    mean_depth_m = round(mean_depth_m, 2),
    min_depth_m = round(min_depth_m, 2),
    max_depth_m = round(max_depth_m, 2),
    depth_range_m = round(depth_range_m, 2)
  ) %>%
  select(
    plot,
    n_depth_markers,
    mean_depth_ft,
    min_depth_ft,
    max_depth_ft,
    depth_range_ft,
    mean_depth_m,
    min_depth_m,
    max_depth_m,
    depth_range_m
  ) %>%
  kable(
    col.names = c(
      "Plot", "Depth markers", "Mean depth (ft)", "Min depth (ft)",
      "Max depth (ft)", "Depth range (ft)", "Mean depth (m)",
      "Min depth (m)", "Max depth (m)", "Depth range (m)"
    )
  )
```

### QA/QC

The full Plot E QA/QC tables are shown in the Main Work Flow tab. These include file checks, interval QA, Genet consistency, and shared-month continuity.

### Cumulative Survivorship

The Plot E cumulative survivorship table and figure are shown in the Main Work Flow tab.

### Interval Survivorship

The Plot E interval survivorship table and figure are shown in the Main Work Flow tab.

### Coral Cover

The Plot E outplant cover table and figure are shown in the Main Work Flow tab.

### Species Prevalence

The Plot E species prevalence table and figure are shown in the Main Work Flow tab.

### Species Cover Composition

The Plot E species cover-composition figure is shown in the Main Work Flow tab.

### Downloads

Use the master tracking dataset and master summary dataset listed in the Home tab for Plot E results.

## Plot F

### Overview

Plot F is included as a placeholder for future outplant match-file analyses.

### Data Status

No Plot F outplant match files are currently configured. Add Plot F rows to `config/outplant_interval_files.csv`, then render this report to populate this tab through the same workflow.

### Depth Metadata

This section will show Plot F corner-marker depth summaries and plot-level depth-gradient context once Plot F outplant match files are configured.

### QA/QC

This section will summarize file checks, missing values, split/fuse labels, Genet consistency, and shared-month continuity once Plot F data are added.

### Cumulative Survivorship

This section will show the percentage of baseline Plot F outplants still present through time.

### Interval Survivorship

This section will show month-to-month Plot F survivorship between adjacent TagLab match files.

### Coral Cover

This section will show Plot F outplant cover through time using the configured plot area.

### Species Prevalence

This section will show Plot F outplant abundance and prevalence by species through time.

### Species Cover Composition

This section will show each species' share of total Plot F outplant cover through time.

### Downloads

This section will point to Plot F processed datasets, summary tables, and figures after Plot F data are configured.

## Plot G

### Overview

Plot G is included as a placeholder for future outplant match-file analyses.

### Data Status

No Plot G outplant match files are currently configured. Add Plot G rows to `config/outplant_interval_files.csv`, then render this report to populate this tab through the same workflow.

### Depth Metadata

This section will show Plot G corner-marker depth summaries and plot-level depth-gradient context once Plot G outplant match files are configured.

### QA/QC

This section will summarize file checks, missing values, split/fuse labels, Genet consistency, and shared-month continuity once Plot G data are added.

### Cumulative Survivorship

This section will show the percentage of baseline Plot G outplants still present through time.

### Interval Survivorship

This section will show month-to-month Plot G survivorship between adjacent TagLab match files.

### Coral Cover

This section will show Plot G outplant cover through time using the configured plot area.

### Species Prevalence

This section will show Plot G outplant abundance and prevalence by species through time.

### Species Cover Composition

This section will show each species' share of total Plot G outplant cover through time.

### Downloads

This section will point to Plot G processed datasets, summary tables, and figures after Plot G data are configured.

## Plot H

### Overview

Plot H is included as a placeholder for future outplant match-file analyses.

### Data Status

No Plot H outplant match files are currently configured. Add Plot H rows to `config/outplant_interval_files.csv`, then render this report to populate this tab through the same workflow.

### Depth Metadata

This section will show Plot H corner-marker depth summaries and plot-level depth-gradient context once Plot H outplant match files are configured.

### QA/QC

This section will summarize file checks, missing values, split/fuse labels, Genet consistency, and shared-month continuity once Plot H data are added.

### Cumulative Survivorship

This section will show the percentage of baseline Plot H outplants still present through time.

### Interval Survivorship

This section will show month-to-month Plot H survivorship between adjacent TagLab match files.

### Coral Cover

This section will show Plot H outplant cover through time using the configured plot area.

### Species Prevalence

This section will show Plot H outplant abundance and prevalence by species through time.

### Species Cover Composition

This section will show each species' share of total Plot H outplant cover through time.

### Downloads

This section will point to Plot H processed datasets, summary tables, and figures after Plot H data are configured.
:::
