---
title: "DPNR Outplant Analyses"
format:
  html:
    theme:
      - cosmo
      - styles.scss
    toc: false
    code-fold: true
    embed-resources: false
    include-in-header:
      text: |
        <style>
        .presentation-hidden {
          display: none !important;
        }
        #TOC {
          display: none !important;
        }
        </style>
execute:
  echo: false
  warning: false
  message: false
---

```{r}
#| label: setup
#| message: false
#| warning: false

library(tidyverse)
library(knitr)

# Find the project folder from the report location. This lets collaborators move
# the full project folder anywhere on their computer and still render the report.
report_path <- knitr::current_input(dir = TRUE)
report_dir <- if (!is.null(report_path)) {
  dirname(normalizePath(report_path, mustWork = TRUE))
} else {
  getwd()
}

project_root <- report_dir
while (!dir.exists(file.path(project_root, "config", "outplant_interval_files"))) {
  parent_dir <- dirname(project_root)
  if (identical(parent_dir, project_root)) {
    stop(
      "Could not find config/outplant_interval_files/. ",
      "Render this report from inside the Coral_survivorship_project folder.",
      call. = FALSE
    )
  }
  project_root <- parent_dir
}

knitr::opts_knit$set(root.dir = project_root)
setwd(project_root)

source(file.path(project_root, "R", "03_outplant_interval_workflow.R"))
```

## Select the Plot that you would like to view

::: panel-tabset
## Home

Data refreshed September 23, 2026: 82 match files across seven plots. Plot F has no supplied match files. Plot E has partial section coverage after January 2026; see its Data Status before comparing later results.

This report analyzes DPNR coral outplant monitoring data from TagLab match files. The workflow is designed for repeated use: add new plot/month files to the config, render the report, review the QA/QC checks, and the tables and figures rebuild automatically.

The active outplant workflow now combines TagLab subsections into one plot-level result for each plot letter. Section-level information is still used for file intake and QA/QC, but survivorship, cover, species prevalence, and species cover composition are summarized for plots A, B, C, D, E, G, and H.

::: {.callout-note appearance="simple"}
### Current data checks

```{r}
#| label: current-intake-qa

tibble(
  check = c("Configured match files", "Missing input files", "Genets with changing species/tag/genotype metadata", "Shared-month missing Genets", "Shared-month new Genets", "Shared-month species mismatches", "Shared-month area mismatches"),
  count = c(nrow(outplant_config), sum(!outplant_file_audit$file_exists), nrow(outplant_genet_consistency_qa), sum(outplant_shared_month_continuity_qa$missing_from_next_start), sum(outplant_shared_month_continuity_qa$new_in_next_start), sum(outplant_shared_month_continuity_qa$species_mismatches), sum(outplant_shared_month_continuity_qa$area_mismatches))
) %>% kable(col.names = c("Check", "Count"))
```

Shared-month differences compare the same survey in adjacent exports. They are review flags, not inferred deaths or corrected records. The existing workflow uses the previous interval's end snapshot for monthly observations; cumulative survivorship depends on consistent Genet identities. Review the QA/QC tables before interpreting these estimates.

### Survey coverage by section

```{r}
#| label: current-section-coverage

outplant_config %>%
  group_by(plot, plot_section) %>%
  summarise(first_survey = min(month_start_date), last_survey = max(month_end_date), match_files = n(), .groups = "drop") %>%
  kable(col.names = c("Plot", "Section", "First survey", "Last survey", "Match files"))
```

## Start with these tabs

-   Use **Analysis Report** for the presentation-ready summary figures and tables.
-   Use the individual **Plot A–E**, **Plot G**, and **Plot H** tabs when checking plot-specific files, QA/QC, and downloads.
-   Use **SOP** when adding new TagLab exports or preparing a GitHub update.
:::

The two recommended datasets to open first are:

-   `data_processed/outplant_master_tracking_dataset.csv`: one row per tracked `Genet` per month, including presence, area, cover contribution, and baseline-survival status.
-   `outputs/Tables/outplant_master_summary_dataset.csv`: one long-format summary table containing cumulative survivorship, interval survivorship, coral cover, species prevalence, and species cover-share metrics.

Each plot tab is organized with the same outline so new data can be added without redesigning the report: overview, data status, depth metadata, QA/QC, cumulative survivorship, interval survivorship, coral cover, species prevalence, species cover composition, and downloads.

## SOP

### Where everything goes

This workflow uses Teams and GitHub for different jobs:

-   **Teams is where we drop off and store the original TagLab exports.** New files go there first, and the Teams copy of `Coral_survivorship_project` can be used to record the filenames in the plot config CSVs.
-   **GitHub is where the working analysis lives.** The code, active config files, approved data, website, and project history are in `CWORI/DPNR_Survivorship`.
-   The Teams project copy is there to help pass files and config information along. We won't render or publish from that copy because it may be a little behind GitHub.
-   Keep the active local Git project outside the Teams/OneDrive-synced folders. This keeps cloud syncing and Git from tripping over each other.
-   Before moving anything to GitHub, make sure it's okay for the repository and doesn't contain anything sensitive.

### Who does what

-   **Anyone working on TagLab:** export the data, put it in the right Teams folder, add the file information to the matching Teams config CSV, and let the Coder know it's ready.
-   **Coder:** move the ready files and rows into the local Git project, render and check everything, and push the update to GitHub.

### Step 1: Export matches from TagLab

1.  Complete annotations and Genet Matching for the relevant plot section and survey months. Make Sure to Add Tag ID from Matches Time Point 1.
2.  Export all months for that plot section through the same TagLab batch/matching process. This is necessary so numeric `Genet` IDs remain consistent between adjacent month files.
3.  Export one matches CSV for each adjacent month pair, such as May-June and June-July.
4.  Confirm the matches export contains the expected fields: `Genet`, `Blob1`, `Blob2`, `Area1`, `Area2`, `Class`, `Action, Tag ID`, and `Split/Fuse`.
5.  Do not rename columns or manually change area values after export.
6.  Make Sure the File Name keeps the two dates. A current example is `1-1_PlotE_Matches_20250507_20250609.csv`.

`Area1` represents the start survey and `Area2` represents the end survey. Match files are the required inputs for the active outplant-survivorship workflow.

### Step 2: Export and archive Genet Data

Genet Data is optional reference metadata; it is not required for the current outplant match workflow.

1.  Export Genet Data when a complete plot-section batch gains new months or when Genet IDs, classes, tags, or other annotations have been corrected.
2.  Use a descriptive name such as `Plot_E_1-0_GenetData_May-August2025.csv`.
3.  Archive it in the Teams `Genet Data` folder under the appropriate plot and section.
4.  Do not add it to the matches config or substitute it for a matches export.

### Step 3: Upload exports to Teams

The Teams intake location is:

`DPNR > Documents > General > Photogrammetry & Monitoring > Survivorship Exports`

Use the two top-level folders shown there:

-   `Matches`: required month-to-month TagLab matches CSVs.
-   `Genet Data`: optional reference/archive exports.

Within each, keep files separated by plot and plot section. Recommended examples are:

-   `Survivorship Exports/Matches/Plot_E/1-0/`
-   `Survivorship Exports/Matches/Plot_E/1-1/`
-   `Survivorship Exports/Genet Data/Plot_E/1-0/`

If you are updating the matches files because you have annotated a new month, remove all of the old one and replace with all new files so that the Genet ID's remain constant.

Before saying the files are ready, check that:

1.  The file is in the correct `Matches` or `Genet Data` folder.
2.  The plot and plot section in the filename/folder are correct.
3.  Both survey dates are visible in the filename or included in the Teams message.
4.  The file is a CSV and opens with the expected columns.
5.  **Previous Files of the same Matches are deleted, DO NOT keep the same file matches if you make a new batch of matches!**
6.  The same interval has not already been uploaded.
7.  Existing exports have not been overwritten or deleted.

### Step 4: Add the file information to the Teams project copy

Use the Teams copy of `Coral_survivorship_project` to record which match files are ready. Only edit the matching plot config under:

`config/outplant_interval_files/`

For example, Plot E files belong in `Plot_E.csv`. Add one row for every month-to-month matches file and keep rows grouped by `plot_section` and ordered by `month_start_date`.

Before anyone starts adding rows, The Coder should make sure the Teams copy has the current `Plot_A.csv` through `Plot_H.csv` structure from GitHub. If the config templates change, we'll first copy over any rows that are still waiting, then refresh the Teams templates. That way nobody's work gets overwritten.

Each row needs:

-   `plot`: display name, such as `Plot E`.
-   `plot_section`: TagLab subsection, such as `1-0` or `1-1`.
-   `plot_folder`: local raw-data folder, such as `Plot_E`.
-   `file`: exact filename, including capitalization and `.csv`.
-   `month_start` and `month_end`: readable survey-month labels.
-   `month_start_date` and `month_end_date`: dates in `YYYY-MM-DD` format.
-   `file_type`: normally `csv`.
-   `match_type`: normally the same value as `plot_section`.
-   `plot_length_m` and `plot_width_m`: plot dimensions in meters.
-   `taglab_area_units`: units used by the TagLab area export, currently `cm2`.

Please leave the header and column names alone, keep Genet Data filenames out of this config, and don't remove existing rows. Editing the Teams config does **not** update the live analysis by itself.

### Step 5: Let Coder know the files are ready

Send Coder a short Teams message with:

-   plot and plot section;
-   start and end survey months/dates;
-   exact matches filename(s);
-   whether a new Genet Data export was included;
-   any known annotation, split/fuse, or export concerns.

Once that message is sent, Coder can move everything into the GitHub project and check it.

### Step 6: Move the ready files into the local Git project

Coder completes these steps on the computer with the local Git project:

1.  Open `Coral_survivorship_project` in RStudio.

2.  Pull the latest GitHub version before copying or editing anything:

    ``` bash
    git pull
    ```

3.  Copy each approved matches CSV from Teams into:

    `data_raw/taglab/Plot_<letter>/`

4.  Open the appropriate local config file under `config/outplant_interval_files/`.

5.  Copy the **new rows** from the Teams config into the local config. Copy the rows rather than replacing the whole local config file.

6.  Confirm that each config filename exactly matches the file placed in `data_raw/taglab/`.

7.  Update `data_raw/metadata/Coordinates_Depths.csv` only when reviewed plot-marker metadata have changed.

### Step 7: Render and validate the Quarto analysis

1.  Open `coral_survivorship_report.qmd` in RStudio.
2.  Click **Render**. Rendering rebuilds the processed datasets, tables, figures, and `docs/` website.
3.  Review the **File Audit** first. Every configured row must show `file_exists = TRUE`.
4.  Review interval QA for missing `Genet`, missing species, negative areas, and unexpected action or split/fuse labels.
5.  Review shared-month continuity. Adjacent intervals should normally show:
    -   zero missing Genets;
    -   zero unexpected new Genets;
    -   zero species mismatches.
6.  Confirm the plot section and month order are correct in tables and figures.
7.  Compare major results with the previous website version and investigate unexplained jumps before publishing.

If a configured file is missing or the identity/continuity checks look strange, pause and check it before pushing.

### Step 8: Commit and push the reviewed update to GitHub

Using the RStudio Git pane:

1.  Review all changed files.
2.  Stage the new raw matches files, changed plot config, updated outputs, and rendered `docs/` files.
3.  Commit with a clear message, for example `Add Plot E 1-0 August-September interval`.
4.  Push the commit to GitHub.

Equivalent R-Studio Terminal commands if that is easier for you are:

``` bash
git status
Rscript scripts/pre_push_check.R
git add .
git commit -m "Describe the plot and interval added"
git push
```

The GitHub repository is `https://github.com/CWORI/DPNR_Survivorship`.

Please make sure this is the repository you are adding too!

### Step 9: Confirm the live website

1.  Wait briefly for GitHub Pages to publish the updated `main/docs` content.
2.  Open `https://cwori.github.io/DPNR_Survivorship/`.
3.  Confirm the new plot/section/month appears and that figures and tables load.
4.  If the website did not update, first confirm that the rendered `docs/` changes were committed and pushed.

### Step 10: Use and share the outputs

-   Use cumulative survivorship as the main survival result.
-   Use interval survivorship as a diagnostic for each month-to-month transition.
-   Start with `data_processed/outplant_master_tracking_dataset.csv` for detailed records.
-   Start with `outputs/Tables/outplant_master_summary_dataset.csv` for combined summary results.
-   Keep the original Teams exports as the untouched archive even after approved copies are added to GitHub.

### Final update checklist

-   [ ] Matches CSV uploaded to the correct Teams plot/section folder.
-   [ ] Optional Genet Data archived separately.
-   [ ] Proposed row added to the correct Teams intake plot config.
-   [ ] Spencer notified that the files are ready.
-   [ ] Latest GitHub project pulled locally.
-   [ ] Approved matches CSV copied into the correct local raw-data folder.
-   [ ] Reviewed config row copied into the correct local plot CSV.
-   [ ] Quarto report rendered successfully.
-   [ ] File audit and QA/QC reviewed.
-   [ ] Changes committed and pushed to GitHub.
-   [ ] Live GitHub Pages website checked.

## Analysis Report

::: {.presentation-hidden}
### Workflow

This report reads the outplant-only TagLab match files listed in the plot-specific CSVs under `config/outplant_interval_files/`, standardizes them into common start/end area columns, collapses repeated blob rows to one tracked `Genet` per interval, and produces plot-level survivorship, cover, and species-composition outputs. TagLab subsections remain available for QA/QC, but the main analysis combines them into one result per plot letter.

The workflow is designed so future users can add new plots or month pairs by editing the config rather than changing analysis code.

The two recommended outplant datasets to open first are:

-   `data_processed/outplant_master_tracking_dataset.csv`: one row per tracked `Genet` per month, including presence, area, cover contribution, and baseline-survival status.
-   `outputs/Tables/outplant_master_summary_dataset.csv`: one long-format summary table containing cumulative survivorship, interval survivorship, coral cover, species prevalence, and species cover-share metrics.

The workflow still writes detailed intermediate CSVs for QA/QC and reproducibility, but most users should only need the two files above unless they are debugging the analysis.

Survivorship is treated as apparent persistence through a TagLab interval: an outplant is counted as surviving when it has measurable area at the start and end of the interval.

### Outplant-Only Workflow

This is the main analysis workflow for the outplant-only TagLab match files. It treats `Area1` as the start-month area and `Area2` as the end-month area, and calculates cover using the configured 16 by 30 m plot area. The same-batch TagLab exports use `Genet` as the across-month tracking ID. If a `Genet` has multiple blob rows in one interval, those rows are collapsed into one tracked outplant before survivorship is calculated. The area unit is read from the appropriate plot CSV under `config/outplant_interval_files/`; the current configuration uses TagLab areas are in square centimeters.

This chunk verifies that every outplant interval file listed in the config exists. This is the first place to check when adding new files for other plots or months.

```{r}
#| label: outplant-file-audit

outplant_file_audit %>%
  select(plot, plot_section, month_start, month_end, match_type, file, file_exists) %>%
  kable(
    col.names = c("Plot", "Section", "Start month", "End month", "Match type", "File", "File exists")
  )
```

This chunk checks whether the TagLab files have missing `Genet` IDs, missing species, negative areas, or unusual action/split-fuse labels. These checks catch export problems before the biological summaries are interpreted.

```{r}
#| label: outplant-interval-qa

outplant_interval_qa %>%
  select(
    plot_section,
    month_start,
    month_end,
    n_rows,
    n_missing_genet,
    n_missing_species,
    n_negative_area_start,
    n_negative_area_end,
    actions,
    split_fuse_events
  ) %>%
  kable(
    col.names = c(
      "Section", "Start month", "End month", "Rows", "Missing Genet", "Missing species",
      "Negative start area", "Negative end area", "Actions", "Split/fuse events"
    )
  )
```

This chunk checks whether the same `Genet` number maps to different species, tags, or genotypes across files. If the table says no conflicts were detected, the same-batch export is behaving much better for individual-level survivorship.

```{r}
#| label: outplant-unstable-genet-examples

if (nrow(outplant_unstable_genet_examples) == 0) {
  tibble(status = "No cross-file Genet identity conflicts detected.") %>%
    kable(col.names = "Status")
} else {
  outplant_unstable_genet_examples %>%
    slice_head(n = 20) %>%
    kable(
      col.names = c(
        "Plot", "Section", "Section label", "Source file", "Start month", "End month", "Genet",
        "Tag", "Genotype", "Species", "Action", "Start area", "End area"
      )
    )
}
```

This chunk checks whether the same shared month matches between adjacent files after repeated `Genet` blob rows have been collapsed. A good export should have zero missing/new Genets and zero species mismatches for each shared month. Area mismatches can occur when TagLab split/fuse behavior changes how multiple blobs are grouped under the same `Genet`.

```{r}
#| label: outplant-shared-month-continuity

outplant_shared_month_continuity_qa %>%
  select(
    plot_section,
    shared_month,
    previous_end_n,
    next_start_n,
    in_both_snapshots,
    missing_from_next_start,
    new_in_next_start,
    species_mismatches,
    area_mismatches,
    max_abs_area_difference
  ) %>%
  mutate(max_abs_area_difference = round(max_abs_area_difference, 4)) %>%
  kable(
    col.names = c(
      "Section", "Shared month", "Previous file end n", "Next file start n",
      "In both", "Missing from next start", "New in next start",
      "Species mismatches", "Area mismatches", "Max area difference"
    )
  )
```

This chunk summarizes cumulative outplant survivorship from the baseline month. Each plot uses the first month with present outplants as the baseline for each monitored subsection, then combines subsections only for months where every configured subsection for that plot is represented. Months with partial subsection coverage are kept in the section-level QA outputs, but are excluded from the full-plot cumulative curve so the denominator does not change through time.
:::

```{r}
#| label: outplant-cumulative-survival-table

outplant_cumulative_survival_summary %>%
  select(
    plot_section_label,
    month,
    baseline_month,
    n_baseline,
    n_died_interval,
    cumulative_deaths_observed,
    n_surviving_from_baseline,
    percent_cumulative_survival,
    percent_cumulative_survival_low,
    percent_cumulative_survival_high
  ) %>%
  mutate(
    percent_cumulative_survival = round(percent_cumulative_survival, 1),
    percent_cumulative_survival_low = round(percent_cumulative_survival_low, 1),
    percent_cumulative_survival_high = round(percent_cumulative_survival_high, 1)
  ) %>%
  kable(
    col.names = c(
      "Plot", "Month", "Baseline month", "Baseline n", "Deaths this interval",
      "Cumulative deaths", "Surviving from baseline",
      "Cumulative survival (%)", "95% CI low", "95% CI high"
    )
  )
```

::: {.presentation-hidden}
This chunk summarizes the Deep Nursery temperature logger data used in the cumulative survivorship figure. The logger is slightly deeper than the outplant site but close enough for this practice overlay.

```{r}
#| label: outplant-temperature-summary

outplant_daily_temperature_summary %>%
  summarise(
    logger_location = first(logger_location),
    start_date = min(date),
    end_date = max(date),
    n_days = n(),
    mean_temperature_c = mean(mean_temperature_c, na.rm = TRUE),
    min_temperature_c = min(min_temperature_c, na.rm = TRUE),
    max_temperature_c = max(max_temperature_c, na.rm = TRUE)
  ) %>%
  mutate(
    mean_temperature_c = round(mean_temperature_c, 2),
    min_temperature_c = round(min_temperature_c, 2),
    max_temperature_c = round(max_temperature_c, 2)
  ) %>%
  kable(
    col.names = c(
      "Logger", "Start date", "End date", "Days",
      "Mean temp (°C)", "Min temp (°C)", "Max temp (°C)"
    )
  )
```
:::

::: {.presentation-hidden}
Plot E has enough monthly observations to work well as a date-based time series. Plots A, B, C, D, G, and H are early monitoring series, so they are shown separately with baseline/follow-up positions instead of being stretched across the full calendar axis.
:::

### Plot E Cumulative Survivorship

```{r}
#| label: outplant-plot-e-cumulative-survival-plot
#| fig-width: 9
#| fig-height: 4.8
#| fig-alt: "Line plot of Plot E cumulative outplant survivorship over survey dates, with points and confidence intervals for each monitoring month and a red temperature overlay."

outplant_plot_cumulative_survival(
  outplant_cumulative_survival_summary %>% filter(plot == "Plot E"),
  outplant_daily_temperature_summary
)
```

### Plots A, B, C, D, G, and H Cumulative Survivorship

```{r}
#| label: outplant-short-cumulative-survival-plot
#| fig-width: 9
#| fig-height: 4.8
#| fig-alt: "Faceted line plot showing Plots A, B, C, D, G, and H cumulative outplant survivorship by baseline and follow-up monitoring step, with confidence intervals."

outplant_plot_short_cumulative_survival(
  outplant_cumulative_survival_summary %>% filter(plot %in% c("Plot A", "Plot B", "Plot C", "Plot D", "Plot G", "Plot H"))
)
```

::: {.presentation-hidden}
This chunk reports interval survivorship between adjacent survey months. It is useful as a diagnostic because a later interval can be 100% even if cumulative survivorship has already declined. Intervals that start before outplanting can have `n_start = 0`; those rows remain in the table but are omitted from interval survival figures because survival cannot be estimated from zero starting corals.
:::

```{r}
#| label: outplant-interval-survival-table

outplant_survival_summary %>%
  select(
    plot_section_label,
    interval_label,
    n_start,
    n_survived,
    n_died,
    n_born,
    percent_survival,
    percent_survival_low,
    percent_survival_high
  ) %>%
  mutate(
    percent_survival = round(percent_survival, 1),
    percent_survival_low = round(percent_survival_low, 1),
    percent_survival_high = round(percent_survival_high, 1)
  ) %>%
  kable(
    col.names = c(
      "Plot", "Interval", "Start n", "Survived n", "Died n", "Born n",
      "Interval survival (%)", "95% CI low", "95% CI high"
    )
  )
```

::: {.presentation-hidden}
Plot E interval survivorship is shown as a time series. Plots A, B, C, D, G, and H are shown with compact bars for their current post-baseline intervals.
:::

### Plot E Interval Survivorship

```{r}
#| label: outplant-plot-e-interval-survival-plot
#| fig-width: 9
#| fig-height: 4.8
#| fig-alt: "Line plot of Plot E interval survivorship between adjacent survey months, with percentage labels and confidence intervals."

outplant_plot_interval_survival(
  outplant_survival_summary %>% filter(plot == "Plot E")
)
```

### Plots A, B, C, D, G, and H Interval Survivorship

```{r}
#| label: outplant-short-interval-survival-plot
#| fig-width: 9
#| fig-height: 4.8
#| fig-alt: "Faceted bar plot showing Plots A, B, C, D, G, and H interval survivorship for post-baseline monitoring intervals, with confidence intervals."

outplant_plot_short_interval_survival(
  outplant_survival_summary %>% filter(plot %in% c("Plot A", "Plot B", "Plot C", "Plot D", "Plot G", "Plot H"))
)
```

::: {.presentation-hidden}
This chunk reports outplant coral cover by month. Cover is calculated as summed outplant area divided by the 480 m2 plot area.
:::

```{r}
#| label: outplant-cover-table

outplant_cover_summary %>%
  select(plot_section_label, month, n_outplants_present, total_outplant_area_m2, plot_area_m2, percent_outplant_cover) %>%
  mutate(
    total_outplant_area_m2 = round(total_outplant_area_m2, 6),
    percent_outplant_cover = round(percent_outplant_cover, 5)
  ) %>%
  kable(
    col.names = c(
      "Plot", "Month", "Outplants present", "Total outplant area (m2)",
      "Plot area (m2)", "Outplant cover (%)"
    )
  )
```

::: {.presentation-hidden}
This chunk plots outplant cover through time. Because outplants are small relative to a 480 m2 plot, the percent cover values are expected to be very small.
:::

```{r}
#| label: outplant-cover-plot
#| fig-width: 8
#| fig-height: 4.8
#| fig-alt: "Line plot of outplant coral cover through time, showing percent of plot area covered by present outplants."

outplant_cover_plot
```

::: {.presentation-hidden}
This chunk summarizes species abundance and prevalence among present outplant annotations in each monthly snapshot. `n_outplants` is the abundance count, and `percent_prevalence` is that species' share of present outplants for that month.
:::

```{r}
#| label: outplant-species-prevalence-table

outplant_species_prevalence_summary %>%
  select(
    plot_section_label,
    month,
    species,
    n_outplants,
    percent_prevalence,
    total_outplant_area_m2,
    percent_cover_within_outplants
  ) %>%
  mutate(
    percent_prevalence = round(percent_prevalence, 1),
    total_outplant_area_m2 = round(total_outplant_area_m2, 6),
    percent_cover_within_outplants = round(percent_cover_within_outplants, 1)
  ) %>%
  kable(
    col.names = c(
      "Plot", "Month", "Species", "Outplant abundance", "Prevalence (%)",
      "Outplant area (m2)", "Share of outplant cover (%)"
    )
  )
```

::: {.presentation-hidden}
This chunk plots species prevalence through time using counts of present outplant annotations.
:::

```{r}
#| label: outplant-species-prevalence-plot
#| fig-width: 8
#| fig-height: 10
#| fig-alt: "Stacked bar plot of outplant species prevalence by survey month, showing each species as a share of present outplant annotations."

outplant_species_prevalence_plot
```

::: {.presentation-hidden}
This chunk plots each species' share of total outplant cover through time. It complements prevalence because a species can have fewer annotations but more cover.
:::

```{r}
#| label: outplant-species-cover-plot
#| fig-width: 8
#| fig-height: 10
#| fig-alt: "Stacked bar plot of outplant cover composition by survey month, showing each species as a share of summed outplant cover."

outplant_species_cover_plot
```

### Outplanted Coral Area by Species

Unlike the composition chart above, this figure shows absolute measured area. It therefore shows whether each species is gaining or losing area even when its percentage of the total stays similar.

```{r}
#| label: outplant-species-area-plot
#| fig-width: 10
#| fig-height: 8
#| fig-alt: "Line charts of measured outplant coral area through time by species and plot."

outplant_species_area_plot
```

### Growth, Loss, and Newly Observed Outplants

This separates each interval's observed area change into growth or shrinkage of corals tracked at both surveys, area that disappears, and area that newly appears. Newly appearing area may be a new outplant, a newly matched annotation, or a plot section returning after a partial survey; the match files alone cannot distinguish those causes.

```{r}
#| label: outplant-cover-change-source-plot
#| fig-width: 10
#| fig-height: 8
#| fig-alt: "Bar charts separating outplant area change into growth or shrinkage, lost area, and newly observed outplants."

outplant_cover_change_source_plot
```

### Area by Genotype

The current TagLab exports include a `genotype` column, but all 7,468 present-outplant records have that field blank. A genotype-area figure cannot be calculated until a genotype value or a Genet-to-genotype lookup table is supplied.

::: presentation-hidden
### Plot Depth Metadata

This chunk summarizes the corner-marker depth metadata for every plot listed in `data_raw/metadata/Coordinates_Depths.csv`. These values describe the plot-level depth context and should not be interpreted as exact depths for individual coral colonies.

```{r}
#| label: outplant-plot-depth-summary

outplant_plot_depth_summary %>%
  mutate(
    mean_depth_ft = round(mean_depth_ft, 1),
    min_depth_ft = round(min_depth_ft, 1),
    max_depth_ft = round(max_depth_ft, 1),
    depth_range_ft = round(depth_range_ft, 1),
    mean_depth_m = round(mean_depth_m, 2),
    min_depth_m = round(min_depth_m, 2),
    max_depth_m = round(max_depth_m, 2),
    depth_range_m = round(depth_range_m, 2),
    centroid_latitude = round(centroid_latitude, 6),
    centroid_longitude = round(centroid_longitude, 6)
  ) %>%
  kable(
    col.names = c(
      "Plot", "Depth markers", "Mean depth (ft)", "Min depth (ft)",
      "Max depth (ft)", "Depth range (ft)", "Mean depth (m)",
      "Min depth (m)", "Max depth (m)", "Depth range (m)",
      "Centroid latitude", "Centroid longitude"
    )
  )
```

This chunk joins the species prevalence results to the plot-level depth summary. It is a setup table for future species-depth analyses once multiple plots have outplant match files configured.

```{r}
#| label: outplant-species-depth-summary

outplant_species_depth_summary %>%
  select(
    plot,
    plot_section,
    month,
    species,
    n_outplants,
    percent_prevalence,
    percent_cover_within_outplants,
    mean_depth_ft,
    min_depth_ft,
    max_depth_ft,
    depth_range_ft
  ) %>%
  mutate(
    percent_prevalence = round(percent_prevalence, 1),
    percent_cover_within_outplants = round(percent_cover_within_outplants, 1),
    mean_depth_ft = round(mean_depth_ft, 1),
    min_depth_ft = round(min_depth_ft, 1),
    max_depth_ft = round(max_depth_ft, 1),
    depth_range_ft = round(depth_range_ft, 1)
  ) %>%
  kable(
    col.names = c(
      "Plot", "Section", "Month", "Species", "Outplant abundance",
      "Prevalence (%)", "Share of outplant cover (%)", "Mean depth (ft)",
      "Min depth (ft)", "Max depth (ft)", "Depth range (ft)"
    )
  )
```
:::

## Plot A

### Overview

Plot A combines the supplied TagLab sections into one plot-level result. Survey dates and section coverage are listed below; baseline survivorship starts at the first survey with present outplants in each section.

### Data Status

<details>
<summary>View source files and survey dates</summary>

The active Plot A files are:

```{r}
#| label: plot-a-configured-files

outplant_config %>%
  filter(plot == "Plot A") %>%
  select(plot, plot_section, month_start, month_end, month_start_date, month_end_date, file, plot_length_m, plot_width_m, taglab_area_units) %>%
  kable(
    col.names = c(
      "Plot", "Section", "Start month", "End month", "Start date", "End date", "File",
      "Plot length (m)", "Plot width (m)", "Area units"
    )
  )
```

</details>

### Depth Metadata

```{r}
#| label: plot-a-depth-summary

outplant_plot_depth_summary %>%
  filter(plot == "Plot A") %>%
  mutate(
    mean_depth_ft = round(mean_depth_ft, 1),
    min_depth_ft = round(min_depth_ft, 1),
    max_depth_ft = round(max_depth_ft, 1),
    depth_range_ft = round(depth_range_ft, 1),
    mean_depth_m = round(mean_depth_m, 2),
    min_depth_m = round(min_depth_m, 2),
    max_depth_m = round(max_depth_m, 2),
    depth_range_m = round(depth_range_m, 2)
  ) %>%
  select(
    plot,
    n_depth_markers,
    mean_depth_ft,
    min_depth_ft,
    max_depth_ft,
    depth_range_ft,
    mean_depth_m,
    min_depth_m,
    max_depth_m,
    depth_range_m
  ) %>%
  kable(
    col.names = c(
      "Plot", "Depth markers", "Mean depth (ft)", "Min depth (ft)",
      "Max depth (ft)", "Depth range (ft)", "Mean depth (m)",
      "Min depth (m)", "Max depth (m)", "Depth range (m)"
    )
  )
```

### QA/QC

<details>
<summary>View quality checks</summary>

```{r}
#| label: plot-a-file-audit

outplant_file_audit %>%
  filter(plot == "Plot A") %>%
  select(plot, plot_section, month_start, month_end, match_type, file, file_exists) %>%
  kable(
    col.names = c("Plot", "Section", "Start month", "End month", "Match type", "File", "File exists")
  )
```

```{r}
#| label: plot-a-interval-qa

outplant_interval_qa %>%
  filter(plot == "Plot A") %>%
  select(
    plot_section,
    month_start,
    month_end,
    n_rows,
    n_missing_genet,
    n_missing_species,
    n_negative_area_start,
    n_negative_area_end,
    actions,
    split_fuse_events
  ) %>%
  kable(
    col.names = c(
      "Section", "Start month", "End month", "Rows", "Missing Genet", "Missing species",
      "Negative start area", "Negative end area", "Actions", "Split/fuse events"
    )
  )
```

```{r}
#| label: plot-a-shared-month-continuity

outplant_shared_month_continuity_qa %>%
  filter(plot == "Plot A") %>%
  select(
    plot_section,
    shared_month,
    previous_end_n,
    next_start_n,
    in_both_snapshots,
    missing_from_next_start,
    new_in_next_start,
    species_mismatches,
    area_mismatches,
    max_abs_area_difference
  ) %>%
  mutate(max_abs_area_difference = round(max_abs_area_difference, 4)) %>%
  kable(
    col.names = c(
      "Section", "Shared month", "Previous file end n", "Next file start n",
      "In both", "Missing from next start", "New in next start",
      "Species mismatches", "Area mismatches", "Max area difference"
    )
  )
```

</details>

### Cumulative Survivorship

```{r}
#| label: plot-a-cumulative-survival-table

outplant_cumulative_survival_summary %>%
  filter(plot == "Plot A") %>%
  select(
    plot_section_label,
    month,
    baseline_month,
    n_baseline,
    n_died_interval,
    cumulative_deaths_observed,
    n_surviving_from_baseline,
    percent_cumulative_survival,
    percent_cumulative_survival_low,
    percent_cumulative_survival_high
  ) %>%
  mutate(
    percent_cumulative_survival = round(percent_cumulative_survival, 1),
    percent_cumulative_survival_low = round(percent_cumulative_survival_low, 1),
    percent_cumulative_survival_high = round(percent_cumulative_survival_high, 1)
  ) %>%
  kable(
    col.names = c(
      "Plot", "Month", "Baseline month", "Baseline n", "Deaths this interval",
      "Cumulative deaths", "Surviving from baseline",
      "Cumulative survival (%)", "95% CI low", "95% CI high"
    )
  )
```

```{r}
#| label: plot-a-cumulative-survival-plot
#| fig-width: 8
#| fig-height: 4.5
#| fig-alt: "Line plot of Plot A cumulative outplant survivorship over survey dates with confidence intervals and temperature overlay."

outplant_plot_cumulative_survival(
  outplant_cumulative_survival_summary %>% filter(plot == "Plot A"),
  outplant_daily_temperature_summary
)
```

### Interval Survivorship

```{r}
#| label: plot-a-interval-survival-table

outplant_survival_summary %>%
  filter(plot == "Plot A") %>%
  select(
    plot_section_label,
    interval_label,
    n_start,
    n_survived,
    n_died,
    n_born,
    percent_survival,
    percent_survival_low,
    percent_survival_high
  ) %>%
  mutate(
    percent_survival = round(percent_survival, 1),
    percent_survival_low = round(percent_survival_low, 1),
    percent_survival_high = round(percent_survival_high, 1)
  ) %>%
  kable(
    col.names = c(
      "Plot", "Interval", "Start n", "Survived n", "Died n", "Born n",
      "Interval survival (%)", "95% CI low", "95% CI high"
    )
  )
```

```{r}
#| label: plot-a-interval-survival-plot
#| fig-width: 8
#| fig-height: 4.5
#| fig-alt: "Line plot of Plot A interval survivorship between adjacent survey months with confidence intervals."

outplant_plot_interval_survival(
  outplant_survival_summary %>% filter(plot == "Plot A")
)
```

### Coral Cover

```{r}
#| label: plot-a-cover-table

outplant_cover_summary %>%
  filter(plot == "Plot A") %>%
  select(plot_section_label, month, n_outplants_present, total_outplant_area_m2, plot_area_m2, percent_outplant_cover) %>%
  mutate(
    total_outplant_area_m2 = round(total_outplant_area_m2, 6),
    percent_outplant_cover = round(percent_outplant_cover, 5)
  ) %>%
  kable(
    col.names = c(
      "Plot", "Month", "Outplants present", "Total outplant area (m2)",
      "Plot area (m2)", "Outplant cover (%)"
    )
  )
```

```{r}
#| label: plot-a-cover-plot
#| fig-width: 8
#| fig-height: 4.5
#| fig-alt: "Line plot of Plot A outplant cover through time as a percent of plot area."

outplant_plot_cover(
  outplant_cover_summary %>% filter(plot == "Plot A")
)
```

### Total Outplant Coral Cover Over Time

```{r}
#| label: plot-a-total-cover-bars
#| fig-width: 9
#| fig-height: 5.5
#| fig-alt: "Bar chart of summed outplant coral cover for Plot A by survey date, distinguishing complete and partial section coverage."

outplant_plot_total_cover_bars(
  outplant_cover_summary %>% filter(plot == "Plot A"),
  outplant_section_monthly_observations %>% filter(plot == "Plot A"),
  outplant_config %>% filter(plot == "Plot A")
)
```

### Species Prevalence

```{r}
#| label: plot-a-species-prevalence-table

outplant_species_prevalence_summary %>%
  filter(plot == "Plot A") %>%
  select(
    plot_section_label,
    month,
    species,
    n_outplants,
    percent_prevalence,
    total_outplant_area_m2,
    percent_cover_within_outplants
  ) %>%
  mutate(
    percent_prevalence = round(percent_prevalence, 1),
    total_outplant_area_m2 = round(total_outplant_area_m2, 6),
    percent_cover_within_outplants = round(percent_cover_within_outplants, 1)
  ) %>%
  kable(
    col.names = c(
      "Plot", "Month", "Species", "Outplant abundance", "Prevalence (%)",
      "Outplant area (m2)", "Share of outplant cover (%)"
    )
  )
```

```{r}
#| label: plot-a-species-prevalence-plot
#| fig-width: 8
#| fig-height: 4.5
#| fig-alt: "Stacked bar plot of Plot A outplant species prevalence by survey month."

outplant_plot_species_prevalence(
  outplant_species_prevalence_summary %>% filter(plot == "Plot A")
)
```

### Species Cover Composition

```{r}
#| label: plot-a-species-cover-plot
#| fig-width: 8
#| fig-height: 4.5
#| fig-alt: "Stacked bar plot of Plot A outplant cover composition by species and survey month."

outplant_plot_species_cover(
  outplant_species_prevalence_summary %>% filter(plot == "Plot A")
)
```

### Outplanted Coral Area by Species

```{r}
#| label: plot-a-species-area-plot
#| fig-width: 8
#| fig-height: 4.8
#| fig-alt: "Line chart of Plot A measured outplant area through time by species."

outplant_plot_species_area(
  outplant_species_area_summary %>% filter(plot == "Plot A")
)
```

### Growth Versus New or Lost Outplants

```{r}
#| label: plot-a-cover-change-source-plot
#| fig-width: 8
#| fig-height: 5
#| fig-alt: "Bar chart separating Plot A area change into growth or shrinkage, lost area, and newly observed outplants."

outplant_plot_cover_change_source(
  outplant_cover_change_source_summary %>% filter(plot == "Plot A")
)
```

### Downloads

Use the master tracking dataset and master summary dataset listed in the Home tab for Plot A results.

## Plot B

### Overview

Plot B combines the supplied TagLab sections into one plot-level result. Survey dates and section coverage are listed below; baseline survivorship starts at the first survey with present outplants in each section.

### Data Status

<details>
<summary>View source files and survey dates</summary>

The active Plot B files are:

```{r}
#| label: plot-b-configured-files

outplant_config %>%
  filter(plot == "Plot B") %>%
  select(plot, plot_section, month_start, month_end, month_start_date, month_end_date, file, plot_length_m, plot_width_m, taglab_area_units) %>%
  kable(
    col.names = c(
      "Plot", "Section", "Start month", "End month", "Start date", "End date", "File",
      "Plot length (m)", "Plot width (m)", "Area units"
    )
  )
```

</details>

### Depth Metadata

```{r}
#| label: plot-b-depth-summary

outplant_plot_depth_summary %>%
  filter(plot == "Plot B") %>%
  mutate(
    mean_depth_ft = round(mean_depth_ft, 1),
    min_depth_ft = round(min_depth_ft, 1),
    max_depth_ft = round(max_depth_ft, 1),
    depth_range_ft = round(depth_range_ft, 1),
    mean_depth_m = round(mean_depth_m, 2),
    min_depth_m = round(min_depth_m, 2),
    max_depth_m = round(max_depth_m, 2),
    depth_range_m = round(depth_range_m, 2)
  ) %>%
  select(
    plot,
    n_depth_markers,
    mean_depth_ft,
    min_depth_ft,
    max_depth_ft,
    depth_range_ft,
    mean_depth_m,
    min_depth_m,
    max_depth_m,
    depth_range_m
  ) %>%
  kable(
    col.names = c(
      "Plot", "Depth markers", "Mean depth (ft)", "Min depth (ft)",
      "Max depth (ft)", "Depth range (ft)", "Mean depth (m)",
      "Min depth (m)", "Max depth (m)", "Depth range (m)"
    )
  )
```

### QA/QC

<details>
<summary>View quality checks</summary>

```{r}
#| label: plot-b-file-audit

outplant_file_audit %>%
  filter(plot == "Plot B") %>%
  select(plot, plot_section, month_start, month_end, match_type, file, file_exists) %>%
  kable(
    col.names = c("Plot", "Section", "Start month", "End month", "Match type", "File", "File exists")
  )
```

```{r}
#| label: plot-b-interval-qa

outplant_interval_qa %>%
  filter(plot == "Plot B") %>%
  select(
    plot_section,
    month_start,
    month_end,
    n_rows,
    n_missing_genet,
    n_missing_species,
    n_negative_area_start,
    n_negative_area_end,
    actions,
    split_fuse_events
  ) %>%
  kable(
    col.names = c(
      "Section", "Start month", "End month", "Rows", "Missing Genet", "Missing species",
      "Negative start area", "Negative end area", "Actions", "Split/fuse events"
    )
  )
```

```{r}
#| label: plot-b-shared-month-continuity

outplant_shared_month_continuity_qa %>%
  filter(plot == "Plot B") %>%
  select(
    plot_section,
    shared_month,
    previous_end_n,
    next_start_n,
    in_both_snapshots,
    missing_from_next_start,
    new_in_next_start,
    species_mismatches,
    area_mismatches,
    max_abs_area_difference
  ) %>%
  mutate(max_abs_area_difference = round(max_abs_area_difference, 4)) %>%
  kable(
    col.names = c(
      "Section", "Shared month", "Previous file end n", "Next file start n",
      "In both", "Missing from next start", "New in next start",
      "Species mismatches", "Area mismatches", "Max area difference"
    )
  )
```

</details>

### Cumulative Survivorship

```{r}
#| label: plot-b-cumulative-survival-table

outplant_cumulative_survival_summary %>%
  filter(plot == "Plot B") %>%
  select(
    plot_section_label,
    month,
    baseline_month,
    n_baseline,
    n_died_interval,
    cumulative_deaths_observed,
    n_surviving_from_baseline,
    percent_cumulative_survival,
    percent_cumulative_survival_low,
    percent_cumulative_survival_high
  ) %>%
  mutate(
    percent_cumulative_survival = round(percent_cumulative_survival, 1),
    percent_cumulative_survival_low = round(percent_cumulative_survival_low, 1),
    percent_cumulative_survival_high = round(percent_cumulative_survival_high, 1)
  ) %>%
  kable(
    col.names = c(
      "Plot", "Month", "Baseline month", "Baseline n", "Deaths this interval",
      "Cumulative deaths", "Surviving from baseline",
      "Cumulative survival (%)", "95% CI low", "95% CI high"
    )
  )
```

```{r}
#| label: plot-b-cumulative-survival-plot
#| fig-width: 8
#| fig-height: 4.5
#| fig-alt: "Line plot of Plot B cumulative outplant survivorship over survey dates with confidence intervals and temperature overlay."

outplant_plot_cumulative_survival(
  outplant_cumulative_survival_summary %>% filter(plot == "Plot B"),
  outplant_daily_temperature_summary
)
```

### Interval Survivorship

```{r}
#| label: plot-b-interval-survival-table

outplant_survival_summary %>%
  filter(plot == "Plot B") %>%
  select(
    plot_section_label,
    interval_label,
    n_start,
    n_survived,
    n_died,
    n_born,
    percent_survival,
    percent_survival_low,
    percent_survival_high
  ) %>%
  mutate(
    percent_survival = round(percent_survival, 1),
    percent_survival_low = round(percent_survival_low, 1),
    percent_survival_high = round(percent_survival_high, 1)
  ) %>%
  kable(
    col.names = c(
      "Plot", "Interval", "Start n", "Survived n", "Died n", "Born n",
      "Interval survival (%)", "95% CI low", "95% CI high"
    )
  )
```

```{r}
#| label: plot-b-interval-survival-plot
#| fig-width: 8
#| fig-height: 4.5
#| fig-alt: "Line plot of Plot B interval survivorship between adjacent survey months with confidence intervals."

outplant_plot_interval_survival(
  outplant_survival_summary %>% filter(plot == "Plot B")
)
```

### Coral Cover

```{r}
#| label: plot-b-cover-table

outplant_cover_summary %>%
  filter(plot == "Plot B") %>%
  select(plot_section_label, month, n_outplants_present, total_outplant_area_m2, plot_area_m2, percent_outplant_cover) %>%
  mutate(
    total_outplant_area_m2 = round(total_outplant_area_m2, 6),
    percent_outplant_cover = round(percent_outplant_cover, 5)
  ) %>%
  kable(
    col.names = c(
      "Plot", "Month", "Outplants present", "Total outplant area (m2)",
      "Plot area (m2)", "Outplant cover (%)"
    )
  )
```

```{r}
#| label: plot-b-cover-plot
#| fig-width: 8
#| fig-height: 4.5
#| fig-alt: "Line plot of Plot B outplant cover through time as a percent of plot area."

outplant_plot_cover(
  outplant_cover_summary %>% filter(plot == "Plot B")
)
```

### Total Outplant Coral Cover Over Time

```{r}
#| label: plot-b-total-cover-bars
#| fig-width: 9
#| fig-height: 5.5
#| fig-alt: "Bar chart of summed outplant coral cover for Plot B by survey date, distinguishing complete and partial section coverage."

outplant_plot_total_cover_bars(
  outplant_cover_summary %>% filter(plot == "Plot B"),
  outplant_section_monthly_observations %>% filter(plot == "Plot B"),
  outplant_config %>% filter(plot == "Plot B")
)
```

### Species Prevalence

```{r}
#| label: plot-b-species-prevalence-table

outplant_species_prevalence_summary %>%
  filter(plot == "Plot B") %>%
  select(
    plot_section_label,
    month,
    species,
    n_outplants,
    percent_prevalence,
    total_outplant_area_m2,
    percent_cover_within_outplants
  ) %>%
  mutate(
    percent_prevalence = round(percent_prevalence, 1),
    total_outplant_area_m2 = round(total_outplant_area_m2, 6),
    percent_cover_within_outplants = round(percent_cover_within_outplants, 1)
  ) %>%
  kable(
    col.names = c(
      "Plot", "Month", "Species", "Outplant abundance", "Prevalence (%)",
      "Outplant area (m2)", "Share of outplant cover (%)"
    )
  )
```

```{r}
#| label: plot-b-species-prevalence-plot
#| fig-width: 8
#| fig-height: 4.5
#| fig-alt: "Stacked bar plot of Plot B outplant species prevalence by survey month."

outplant_plot_species_prevalence(
  outplant_species_prevalence_summary %>% filter(plot == "Plot B")
)
```

### Species Cover Composition

```{r}
#| label: plot-b-species-cover-plot
#| fig-width: 8
#| fig-height: 4.5
#| fig-alt: "Stacked bar plot of Plot B outplant cover composition by species and survey month."

outplant_plot_species_cover(
  outplant_species_prevalence_summary %>% filter(plot == "Plot B")
)
```

### Outplanted Coral Area by Species

```{r}
#| label: plot-b-species-area-plot
#| fig-width: 8
#| fig-height: 4.8
#| fig-alt: "Line chart of Plot B measured outplant area through time by species."

outplant_plot_species_area(
  outplant_species_area_summary %>% filter(plot == "Plot B")
)
```

### Growth Versus New or Lost Outplants

```{r}
#| label: plot-b-cover-change-source-plot
#| fig-width: 8
#| fig-height: 5
#| fig-alt: "Bar chart separating Plot B area change into growth or shrinkage, lost area, and newly observed outplants."

outplant_plot_cover_change_source(
  outplant_cover_change_source_summary %>% filter(plot == "Plot B")
)
```

### Downloads

Use the master tracking dataset and master summary dataset listed in the Home tab for Plot B results.

## Plot C

### Overview

Plot C now includes outplant match-file analyses for sections 0-0 and 1-0, combined into one Plot C result. The supplied surveys span November 2025 through August 2026. Baseline survivorship starts at the first survey with present outplants in each section.

### Data Status

<details>
<summary>View source files and survey dates</summary>

The active Plot C files are:

```{r}
#| label: plot-c-configured-files

outplant_config %>%
  filter(plot == "Plot C") %>%
  select(plot, plot_section, month_start, month_end, month_start_date, month_end_date, file, plot_length_m, plot_width_m, taglab_area_units) %>%
  kable(
    col.names = c(
      "Plot", "Section", "Start month", "End month", "Start date", "End date", "File",
      "Plot length (m)", "Plot width (m)", "Area units"
    )
  )
```

</details>

### Depth Metadata

```{r}
#| label: plot-c-depth-summary

outplant_plot_depth_summary %>%
  filter(plot == "Plot C") %>%
  mutate(
    mean_depth_ft = round(mean_depth_ft, 1),
    min_depth_ft = round(min_depth_ft, 1),
    max_depth_ft = round(max_depth_ft, 1),
    depth_range_ft = round(depth_range_ft, 1),
    mean_depth_m = round(mean_depth_m, 2),
    min_depth_m = round(min_depth_m, 2),
    max_depth_m = round(max_depth_m, 2),
    depth_range_m = round(depth_range_m, 2)
  ) %>%
  select(
    plot,
    n_depth_markers,
    mean_depth_ft,
    min_depth_ft,
    max_depth_ft,
    depth_range_ft,
    mean_depth_m,
    min_depth_m,
    max_depth_m,
    depth_range_m
  ) %>%
  kable(
    col.names = c(
      "Plot", "Depth markers", "Mean depth (ft)", "Min depth (ft)",
      "Max depth (ft)", "Depth range (ft)", "Mean depth (m)",
      "Min depth (m)", "Max depth (m)", "Depth range (m)"
    )
  )
```

### QA/QC

<details>
<summary>View quality checks</summary>

```{r}
#| label: plot-c-file-audit

outplant_file_audit %>%
  filter(plot == "Plot C") %>%
  select(plot, plot_section, month_start, month_end, match_type, file, file_exists) %>%
  kable(
    col.names = c("Plot", "Section", "Start month", "End month", "Match type", "File", "File exists")
  )
```

```{r}
#| label: plot-c-interval-qa

outplant_interval_qa %>%
  filter(plot == "Plot C") %>%
  select(
    plot_section,
    month_start,
    month_end,
    n_rows,
    n_missing_genet,
    n_missing_species,
    n_negative_area_start,
    n_negative_area_end,
    actions,
    split_fuse_events
  ) %>%
  kable(
    col.names = c(
      "Section", "Start month", "End month", "Rows", "Missing Genet", "Missing species",
      "Negative start area", "Negative end area", "Actions", "Split/fuse events"
    )
  )
```

```{r}
#| label: plot-c-shared-month-continuity

outplant_shared_month_continuity_qa %>%
  filter(plot == "Plot C") %>%
  select(
    plot_section,
    shared_month,
    previous_end_n,
    next_start_n,
    in_both_snapshots,
    missing_from_next_start,
    new_in_next_start,
    species_mismatches,
    area_mismatches,
    max_abs_area_difference
  ) %>%
  mutate(max_abs_area_difference = round(max_abs_area_difference, 4)) %>%
  kable(
    col.names = c(
      "Section", "Shared month", "Previous file end n", "Next file start n",
      "In both", "Missing from next start", "New in next start",
      "Species mismatches", "Area mismatches", "Max area difference"
    )
  )
```

</details>

### Cumulative Survivorship

```{r}
#| label: plot-c-cumulative-survival-table

outplant_cumulative_survival_summary %>%
  filter(plot == "Plot C") %>%
  select(
    plot_section_label,
    month,
    baseline_month,
    n_baseline,
    n_died_interval,
    cumulative_deaths_observed,
    n_surviving_from_baseline,
    percent_cumulative_survival,
    percent_cumulative_survival_low,
    percent_cumulative_survival_high
  ) %>%
  mutate(
    percent_cumulative_survival = round(percent_cumulative_survival, 1),
    percent_cumulative_survival_low = round(percent_cumulative_survival_low, 1),
    percent_cumulative_survival_high = round(percent_cumulative_survival_high, 1)
  ) %>%
  kable(
    col.names = c(
      "Plot", "Month", "Baseline month", "Baseline n", "Deaths this interval",
      "Cumulative deaths", "Surviving from baseline",
      "Cumulative survival (%)", "95% CI low", "95% CI high"
    )
  )
```

```{r}
#| label: plot-c-cumulative-survival-plot
#| fig-width: 8
#| fig-height: 4.5
#| fig-alt: "Line plot of Plot C cumulative outplant survivorship over survey dates with confidence intervals and temperature overlay."

outplant_plot_cumulative_survival(
  outplant_cumulative_survival_summary %>% filter(plot == "Plot C"),
  outplant_daily_temperature_summary
)
```

### Interval Survivorship

```{r}
#| label: plot-c-interval-survival-table

outplant_survival_summary %>%
  filter(plot == "Plot C") %>%
  select(
    plot_section_label,
    interval_label,
    n_start,
    n_survived,
    n_died,
    n_born,
    percent_survival,
    percent_survival_low,
    percent_survival_high
  ) %>%
  mutate(
    percent_survival = round(percent_survival, 1),
    percent_survival_low = round(percent_survival_low, 1),
    percent_survival_high = round(percent_survival_high, 1)
  ) %>%
  kable(
    col.names = c(
      "Plot", "Interval", "Start n", "Survived n", "Died n", "Born n",
      "Interval survival (%)", "95% CI low", "95% CI high"
    )
  )
```

```{r}
#| label: plot-c-interval-survival-plot
#| fig-width: 8
#| fig-height: 4.5
#| fig-alt: "Line plot of Plot C interval survivorship between adjacent survey months with confidence intervals."

outplant_plot_interval_survival(
  outplant_survival_summary %>% filter(plot == "Plot C")
)
```

### Coral Cover

```{r}
#| label: plot-c-cover-table

outplant_cover_summary %>%
  filter(plot == "Plot C") %>%
  select(plot_section_label, month, n_outplants_present, total_outplant_area_m2, plot_area_m2, percent_outplant_cover) %>%
  mutate(
    total_outplant_area_m2 = round(total_outplant_area_m2, 6),
    percent_outplant_cover = round(percent_outplant_cover, 5)
  ) %>%
  kable(
    col.names = c(
      "Plot", "Month", "Outplants present", "Total outplant area (m2)",
      "Plot area (m2)", "Outplant cover (%)"
    )
  )
```

```{r}
#| label: plot-c-cover-plot
#| fig-width: 8
#| fig-height: 4.5
#| fig-alt: "Line plot of Plot C outplant cover through time as a percent of plot area."

outplant_plot_cover(
  outplant_cover_summary %>% filter(plot == "Plot C")
)
```

### Total Outplant Coral Cover Over Time

```{r}
#| label: plot-c-total-cover-bars
#| fig-width: 9
#| fig-height: 5.5
#| fig-alt: "Bar chart of summed outplant coral cover for Plot C by survey date, distinguishing complete and partial section coverage."

outplant_plot_total_cover_bars(
  outplant_cover_summary %>% filter(plot == "Plot C"),
  outplant_section_monthly_observations %>% filter(plot == "Plot C"),
  outplant_config %>% filter(plot == "Plot C")
)
```

### Species Prevalence

```{r}
#| label: plot-c-species-prevalence-table

outplant_species_prevalence_summary %>%
  filter(plot == "Plot C") %>%
  select(
    plot_section_label,
    month,
    species,
    n_outplants,
    percent_prevalence,
    total_outplant_area_m2,
    percent_cover_within_outplants
  ) %>%
  mutate(
    percent_prevalence = round(percent_prevalence, 1),
    total_outplant_area_m2 = round(total_outplant_area_m2, 6),
    percent_cover_within_outplants = round(percent_cover_within_outplants, 1)
  ) %>%
  kable(
    col.names = c(
      "Plot", "Month", "Species", "Outplant abundance", "Prevalence (%)",
      "Outplant area (m2)", "Share of outplant cover (%)"
    )
  )
```

```{r}
#| label: plot-c-species-prevalence-plot
#| fig-width: 8
#| fig-height: 4.5
#| fig-alt: "Stacked bar plot of Plot C outplant species prevalence by survey month."

outplant_plot_species_prevalence(
  outplant_species_prevalence_summary %>% filter(plot == "Plot C")
)
```

### Species Cover Composition

```{r}
#| label: plot-c-species-cover-plot
#| fig-width: 8
#| fig-height: 4.5
#| fig-alt: "Stacked bar plot of Plot C outplant cover composition by species and survey month."

outplant_plot_species_cover(
  outplant_species_prevalence_summary %>% filter(plot == "Plot C")
)
```

### Outplanted Coral Area by Species

```{r}
#| label: plot-c-species-area-plot
#| fig-width: 8
#| fig-height: 4.8
#| fig-alt: "Line chart of Plot C measured outplant area through time by species."

outplant_plot_species_area(
  outplant_species_area_summary %>% filter(plot == "Plot C")
)
```

### Growth Versus New or Lost Outplants

```{r}
#| label: plot-c-cover-change-source-plot
#| fig-width: 8
#| fig-height: 5
#| fig-alt: "Bar chart separating Plot C area change into growth or shrinkage, lost area, and newly observed outplants."

outplant_plot_cover_change_source(
  outplant_cover_change_source_summary %>% filter(plot == "Plot C")
)
```

### Downloads

Use the master tracking dataset and master summary dataset listed in the Home tab for Plot C results.

## Plot D

### Overview

Plot D combines the supplied TagLab sections into one plot-level result. Survey dates and section coverage are listed below; baseline survivorship starts at the first survey with present outplants in each section.

### Data Status

<details>
<summary>View source files and survey dates</summary>

The active Plot D files are:

```{r}
#| label: plot-d-configured-files

outplant_config %>%
  filter(plot == "Plot D") %>%
  select(plot, plot_section, month_start, month_end, month_start_date, month_end_date, file, plot_length_m, plot_width_m, taglab_area_units) %>%
  kable(
    col.names = c(
      "Plot", "Section", "Start month", "End month", "Start date", "End date", "File",
      "Plot length (m)", "Plot width (m)", "Area units"
    )
  )
```

</details>

### Depth Metadata

```{r}
#| label: plot-d-depth-summary

outplant_plot_depth_summary %>%
  filter(plot == "Plot D") %>%
  mutate(
    mean_depth_ft = round(mean_depth_ft, 1),
    min_depth_ft = round(min_depth_ft, 1),
    max_depth_ft = round(max_depth_ft, 1),
    depth_range_ft = round(depth_range_ft, 1),
    mean_depth_m = round(mean_depth_m, 2),
    min_depth_m = round(min_depth_m, 2),
    max_depth_m = round(max_depth_m, 2),
    depth_range_m = round(depth_range_m, 2)
  ) %>%
  select(
    plot,
    n_depth_markers,
    mean_depth_ft,
    min_depth_ft,
    max_depth_ft,
    depth_range_ft,
    mean_depth_m,
    min_depth_m,
    max_depth_m,
    depth_range_m
  ) %>%
  kable(
    col.names = c(
      "Plot", "Depth markers", "Mean depth (ft)", "Min depth (ft)",
      "Max depth (ft)", "Depth range (ft)", "Mean depth (m)",
      "Min depth (m)", "Max depth (m)", "Depth range (m)"
    )
  )
```

### QA/QC

<details>
<summary>View quality checks</summary>

```{r}
#| label: plot-d-file-audit

outplant_file_audit %>%
  filter(plot == "Plot D") %>%
  select(plot, plot_section, month_start, month_end, match_type, file, file_exists) %>%
  kable(
    col.names = c("Plot", "Section", "Start month", "End month", "Match type", "File", "File exists")
  )
```

```{r}
#| label: plot-d-interval-qa

outplant_interval_qa %>%
  filter(plot == "Plot D") %>%
  select(
    plot_section,
    month_start,
    month_end,
    n_rows,
    n_missing_genet,
    n_missing_species,
    n_negative_area_start,
    n_negative_area_end,
    actions,
    split_fuse_events
  ) %>%
  kable(
    col.names = c(
      "Section", "Start month", "End month", "Rows", "Missing Genet", "Missing species",
      "Negative start area", "Negative end area", "Actions", "Split/fuse events"
    )
  )
```

```{r}
#| label: plot-d-shared-month-continuity

outplant_shared_month_continuity_qa %>%
  filter(plot == "Plot D") %>%
  select(
    plot_section,
    shared_month,
    previous_end_n,
    next_start_n,
    in_both_snapshots,
    missing_from_next_start,
    new_in_next_start,
    species_mismatches,
    area_mismatches,
    max_abs_area_difference
  ) %>%
  mutate(max_abs_area_difference = round(max_abs_area_difference, 4)) %>%
  kable(
    col.names = c(
      "Section", "Shared month", "Previous file end n", "Next file start n",
      "In both", "Missing from next start", "New in next start",
      "Species mismatches", "Area mismatches", "Max area difference"
    )
  )
```

</details>

### Cumulative Survivorship

```{r}
#| label: plot-d-cumulative-survival-table

outplant_cumulative_survival_summary %>%
  filter(plot == "Plot D") %>%
  select(
    plot_section_label,
    month,
    baseline_month,
    n_baseline,
    n_died_interval,
    cumulative_deaths_observed,
    n_surviving_from_baseline,
    percent_cumulative_survival,
    percent_cumulative_survival_low,
    percent_cumulative_survival_high
  ) %>%
  mutate(
    percent_cumulative_survival = round(percent_cumulative_survival, 1),
    percent_cumulative_survival_low = round(percent_cumulative_survival_low, 1),
    percent_cumulative_survival_high = round(percent_cumulative_survival_high, 1)
  ) %>%
  kable(
    col.names = c(
      "Plot", "Month", "Baseline month", "Baseline n", "Deaths this interval",
      "Cumulative deaths", "Surviving from baseline",
      "Cumulative survival (%)", "95% CI low", "95% CI high"
    )
  )
```

```{r}
#| label: plot-d-cumulative-survival-plot
#| fig-width: 8
#| fig-height: 4.5
#| fig-alt: "Line plot of Plot D cumulative outplant survivorship over survey dates with confidence intervals and temperature overlay."

outplant_plot_cumulative_survival(
  outplant_cumulative_survival_summary %>% filter(plot == "Plot D"),
  outplant_daily_temperature_summary
)
```

### Interval Survivorship

```{r}
#| label: plot-d-interval-survival-table

outplant_survival_summary %>%
  filter(plot == "Plot D") %>%
  select(
    plot_section_label,
    interval_label,
    n_start,
    n_survived,
    n_died,
    n_born,
    percent_survival,
    percent_survival_low,
    percent_survival_high
  ) %>%
  mutate(
    percent_survival = round(percent_survival, 1),
    percent_survival_low = round(percent_survival_low, 1),
    percent_survival_high = round(percent_survival_high, 1)
  ) %>%
  kable(
    col.names = c(
      "Plot", "Interval", "Start n", "Survived n", "Died n", "Born n",
      "Interval survival (%)", "95% CI low", "95% CI high"
    )
  )
```

```{r}
#| label: plot-d-interval-survival-plot
#| fig-width: 8
#| fig-height: 4.5
#| fig-alt: "Line plot of Plot D interval survivorship between adjacent survey months with confidence intervals."

outplant_plot_interval_survival(
  outplant_survival_summary %>% filter(plot == "Plot D")
)
```

### Coral Cover

```{r}
#| label: plot-d-cover-table

outplant_cover_summary %>%
  filter(plot == "Plot D") %>%
  select(plot_section_label, month, n_outplants_present, total_outplant_area_m2, plot_area_m2, percent_outplant_cover) %>%
  mutate(
    total_outplant_area_m2 = round(total_outplant_area_m2, 6),
    percent_outplant_cover = round(percent_outplant_cover, 5)
  ) %>%
  kable(
    col.names = c(
      "Plot", "Month", "Outplants present", "Total outplant area (m2)",
      "Plot area (m2)", "Outplant cover (%)"
    )
  )
```

```{r}
#| label: plot-d-cover-plot
#| fig-width: 8
#| fig-height: 4.5
#| fig-alt: "Line plot of Plot D outplant cover through time as a percent of plot area."

outplant_plot_cover(
  outplant_cover_summary %>% filter(plot == "Plot D")
)
```

### Total Outplant Coral Cover Over Time

```{r}
#| label: plot-d-total-cover-bars
#| fig-width: 9
#| fig-height: 5.5
#| fig-alt: "Bar chart of summed outplant coral cover for Plot D by survey date, distinguishing complete and partial section coverage."

outplant_plot_total_cover_bars(
  outplant_cover_summary %>% filter(plot == "Plot D"),
  outplant_section_monthly_observations %>% filter(plot == "Plot D"),
  outplant_config %>% filter(plot == "Plot D")
)
```

### Species Prevalence

```{r}
#| label: plot-d-species-prevalence-table

outplant_species_prevalence_summary %>%
  filter(plot == "Plot D") %>%
  select(
    plot_section_label,
    month,
    species,
    n_outplants,
    percent_prevalence,
    total_outplant_area_m2,
    percent_cover_within_outplants
  ) %>%
  mutate(
    percent_prevalence = round(percent_prevalence, 1),
    total_outplant_area_m2 = round(total_outplant_area_m2, 6),
    percent_cover_within_outplants = round(percent_cover_within_outplants, 1)
  ) %>%
  kable(
    col.names = c(
      "Plot", "Month", "Species", "Outplant abundance", "Prevalence (%)",
      "Outplant area (m2)", "Share of outplant cover (%)"
    )
  )
```

```{r}
#| label: plot-d-species-prevalence-plot
#| fig-width: 8
#| fig-height: 4.5
#| fig-alt: "Stacked bar plot of Plot D outplant species prevalence by survey month."

outplant_plot_species_prevalence(
  outplant_species_prevalence_summary %>% filter(plot == "Plot D")
)
```

### Species Cover Composition

```{r}
#| label: plot-d-species-cover-plot
#| fig-width: 8
#| fig-height: 4.5
#| fig-alt: "Stacked bar plot of Plot D outplant cover composition by species and survey month."

outplant_plot_species_cover(
  outplant_species_prevalence_summary %>% filter(plot == "Plot D")
)
```

### Outplanted Coral Area by Species

```{r}
#| label: plot-d-species-area-plot
#| fig-width: 8
#| fig-height: 4.8
#| fig-alt: "Line chart of Plot D measured outplant area through time by species."

outplant_plot_species_area(
  outplant_species_area_summary %>% filter(plot == "Plot D")
)
```

### Growth Versus New or Lost Outplants

```{r}
#| label: plot-d-cover-change-source-plot
#| fig-width: 8
#| fig-height: 5
#| fig-alt: "Bar chart separating Plot D area change into growth or shrinkage, lost area, and newly observed outplants."

outplant_plot_cover_change_source(
  outplant_cover_change_source_summary %>% filter(plot == "Plot D")
)
```

### Downloads

Use the master tracking dataset and master summary dataset listed in the Home tab for Plot D results.

## Plot E

### Overview

Plot E is currently the longest configured plot for the outplant-only TagLab match workflow. Sections 0-0, 0-1, 1-0, and 1-1 are included. All four sections extend through January 20, 2026; only 0-0 and 0-1 continue through May 4, 2026. Full-plot cumulative survivorship stops in January. Later cover, interval-survival, and species summaries describe only the available sections and must not be interpreted as complete-plot changes.

### Data Status

<details>
<summary>View source files and survey dates</summary>

The active Plot E files are:

```{r}
#| label: plot-e-configured-files

outplant_config %>%
  filter(plot == "Plot E") %>%
  select(plot, plot_section, month_start, month_end, month_start_date, month_end_date, file, plot_length_m, plot_width_m, taglab_area_units) %>%
  kable(
    col.names = c(
      "Plot", "Section", "Start month", "End month", "Start date", "End date", "File",
      "Plot length (m)", "Plot width (m)", "Area units"
    )
  )
```

</details>

### Depth Metadata

```{r}
#| label: plot-e-depth-summary

outplant_plot_depth_summary %>%
  filter(plot == "Plot E") %>%
  mutate(
    mean_depth_ft = round(mean_depth_ft, 1),
    min_depth_ft = round(min_depth_ft, 1),
    max_depth_ft = round(max_depth_ft, 1),
    depth_range_ft = round(depth_range_ft, 1),
    mean_depth_m = round(mean_depth_m, 2),
    min_depth_m = round(min_depth_m, 2),
    max_depth_m = round(max_depth_m, 2),
    depth_range_m = round(depth_range_m, 2)
  ) %>%
  select(
    plot,
    n_depth_markers,
    mean_depth_ft,
    min_depth_ft,
    max_depth_ft,
    depth_range_ft,
    mean_depth_m,
    min_depth_m,
    max_depth_m,
    depth_range_m
  ) %>%
  kable(
    col.names = c(
      "Plot", "Depth markers", "Mean depth (ft)", "Min depth (ft)",
      "Max depth (ft)", "Depth range (ft)", "Mean depth (m)",
      "Min depth (m)", "Max depth (m)", "Depth range (m)"
    )
  )
```

### QA/QC

<details>
<summary>View quality checks</summary>

```{r}
#| label: plot-e-file-audit

outplant_file_audit %>%
  filter(plot == "Plot E") %>%
  select(plot, plot_section, month_start, month_end, match_type, file, file_exists) %>%
  kable(
    col.names = c("Plot", "Section", "Start month", "End month", "Match type", "File", "File exists")
  )
```

```{r}
#| label: plot-e-interval-qa

outplant_interval_qa %>%
  filter(plot == "Plot E") %>%
  select(
    plot_section,
    month_start,
    month_end,
    n_rows,
    n_missing_genet,
    n_missing_species,
    n_negative_area_start,
    n_negative_area_end,
    actions,
    split_fuse_events
  ) %>%
  kable(
    col.names = c(
      "Section", "Start month", "End month", "Rows", "Missing Genet", "Missing species",
      "Negative start area", "Negative end area", "Actions", "Split/fuse events"
    )
  )
```

```{r}
#| label: plot-e-shared-month-continuity

outplant_shared_month_continuity_qa %>%
  filter(plot == "Plot E") %>%
  select(
    plot_section,
    shared_month,
    previous_end_n,
    next_start_n,
    in_both_snapshots,
    missing_from_next_start,
    new_in_next_start,
    species_mismatches,
    area_mismatches,
    max_abs_area_difference
  ) %>%
  mutate(max_abs_area_difference = round(max_abs_area_difference, 4)) %>%
  kable(
    col.names = c(
      "Section", "Shared month", "Previous file end n", "Next file start n",
      "In both", "Missing from next start", "New in next start",
      "Species mismatches", "Area mismatches", "Max area difference"
    )
  )
```

</details>

### Cumulative Survivorship

```{r}
#| label: plot-e-cumulative-survival-table

outplant_cumulative_survival_summary %>%
  filter(plot == "Plot E") %>%
  select(
    plot_section_label,
    month,
    baseline_month,
    n_baseline,
    n_died_interval,
    cumulative_deaths_observed,
    n_surviving_from_baseline,
    percent_cumulative_survival,
    percent_cumulative_survival_low,
    percent_cumulative_survival_high
  ) %>%
  mutate(
    percent_cumulative_survival = round(percent_cumulative_survival, 1),
    percent_cumulative_survival_low = round(percent_cumulative_survival_low, 1),
    percent_cumulative_survival_high = round(percent_cumulative_survival_high, 1)
  ) %>%
  kable(
    col.names = c(
      "Plot", "Month", "Baseline month", "Baseline n", "Deaths this interval",
      "Cumulative deaths", "Surviving from baseline",
      "Cumulative survival (%)", "95% CI low", "95% CI high"
    )
  )
```

```{r}
#| label: plot-e-cumulative-survival-plot
#| fig-width: 8
#| fig-height: 4.5
#| fig-alt: "Line plot of Plot E cumulative outplant survivorship over survey dates with confidence intervals and temperature overlay."

outplant_plot_cumulative_survival(
  outplant_cumulative_survival_summary %>% filter(plot == "Plot E"),
  outplant_daily_temperature_summary
)
```

### Interval Survivorship

```{r}
#| label: plot-e-interval-survival-table

outplant_survival_summary %>%
  filter(plot == "Plot E") %>%
  select(
    plot_section_label,
    interval_label,
    n_start,
    n_survived,
    n_died,
    n_born,
    percent_survival,
    percent_survival_low,
    percent_survival_high
  ) %>%
  mutate(
    percent_survival = round(percent_survival, 1),
    percent_survival_low = round(percent_survival_low, 1),
    percent_survival_high = round(percent_survival_high, 1)
  ) %>%
  kable(
    col.names = c(
      "Plot", "Interval", "Start n", "Survived n", "Died n", "Born n",
      "Interval survival (%)", "95% CI low", "95% CI high"
    )
  )
```

```{r}
#| label: plot-e-interval-survival-plot
#| fig-width: 8
#| fig-height: 4.5
#| fig-alt: "Line plot of Plot E interval survivorship between adjacent survey months with confidence intervals."

outplant_plot_interval_survival(
  outplant_survival_summary %>% filter(plot == "Plot E")
)
```

### Coral Cover

```{r}
#| label: plot-e-cover-table

outplant_cover_summary %>%
  filter(plot == "Plot E") %>%
  select(plot_section_label, month, n_outplants_present, total_outplant_area_m2, plot_area_m2, percent_outplant_cover) %>%
  mutate(
    total_outplant_area_m2 = round(total_outplant_area_m2, 6),
    percent_outplant_cover = round(percent_outplant_cover, 5)
  ) %>%
  kable(
    col.names = c(
      "Plot", "Month", "Outplants present", "Total outplant area (m2)",
      "Plot area (m2)", "Outplant cover (%)"
    )
  )
```

```{r}
#| label: plot-e-cover-plot
#| fig-width: 8
#| fig-height: 4.5
#| fig-alt: "Line plot of Plot E outplant cover through time as a percent of plot area."

outplant_plot_cover(
  outplant_cover_summary %>% filter(plot == "Plot E")
)
```

### Total Outplant Coral Cover Over Time

```{r}
#| label: plot-e-total-cover-bars
#| fig-width: 9
#| fig-height: 5.5
#| fig-alt: "Bar chart of summed outplant coral cover for Plot E by survey date, distinguishing complete and partial section coverage."

outplant_plot_total_cover_bars(
  outplant_cover_summary %>% filter(plot == "Plot E"),
  outplant_section_monthly_observations %>% filter(plot == "Plot E"),
  outplant_config %>% filter(plot == "Plot E")
)
```

### Species Prevalence

```{r}
#| label: plot-e-species-prevalence-table

outplant_species_prevalence_summary %>%
  filter(plot == "Plot E") %>%
  select(
    plot_section_label,
    month,
    species,
    n_outplants,
    percent_prevalence,
    total_outplant_area_m2,
    percent_cover_within_outplants
  ) %>%
  mutate(
    percent_prevalence = round(percent_prevalence, 1),
    total_outplant_area_m2 = round(total_outplant_area_m2, 6),
    percent_cover_within_outplants = round(percent_cover_within_outplants, 1)
  ) %>%
  kable(
    col.names = c(
      "Plot", "Month", "Species", "Outplant abundance", "Prevalence (%)",
      "Outplant area (m2)", "Share of outplant cover (%)"
    )
  )
```

```{r}
#| label: plot-e-species-prevalence-plot
#| fig-width: 8
#| fig-height: 4.5
#| fig-alt: "Stacked bar plot of Plot E outplant species prevalence by survey month."

outplant_plot_species_prevalence(
  outplant_species_prevalence_summary %>% filter(plot == "Plot E")
)
```

### Species Cover Composition

```{r}
#| label: plot-e-species-cover-plot
#| fig-width: 8
#| fig-height: 4.5
#| fig-alt: "Stacked bar plot of Plot E outplant cover composition by species and survey month."

outplant_plot_species_cover(
  outplant_species_prevalence_summary %>% filter(plot == "Plot E")
)
```

### Outplanted Coral Area by Species

```{r}
#| label: plot-e-species-area-plot
#| fig-width: 8
#| fig-height: 4.8
#| fig-alt: "Line chart of Plot E measured outplant area through time by species."

outplant_plot_species_area(
  outplant_species_area_summary %>% filter(plot == "Plot E")
)
```

### Growth Versus New or Lost Outplants

```{r}
#| label: plot-e-cover-change-source-plot
#| fig-width: 8
#| fig-height: 5
#| fig-alt: "Bar chart separating Plot E area change into growth or shrinkage, lost area, and newly observed outplants."

outplant_plot_cover_change_source(
  outplant_cover_change_source_summary %>% filter(plot == "Plot E")
)
```

### Downloads

Use the master tracking dataset and master summary dataset listed in the Home tab for Plot E results.

## Plot F

### Overview

Plot F is included as a placeholder for future outplant match-file analyses.

### Data Status

<details>
<summary>View source files and survey dates</summary>

No Plot F outplant match files are currently configured. Add rows to `config/outplant_interval_files/Plot_F.csv`, then render this report to populate this tab through the same workflow.

</details>

### Depth Metadata

This section will show Plot F corner-marker depth summaries and plot-level depth-gradient context once Plot F outplant match files are configured.

### QA/QC

<details>
<summary>View quality checks</summary>

This section will summarize file checks, missing values, split/fuse labels, Genet consistency, and shared-month continuity once Plot F data are added.

</details>

### Cumulative Survivorship

This section will show the percentage of baseline Plot F outplants still present through time.

### Interval Survivorship

This section will show month-to-month Plot F survivorship between adjacent TagLab match files.

### Coral Cover

This section will show Plot F outplant cover through time using the configured plot area.

### Species Prevalence

This section will show Plot F outplant abundance and prevalence by species through time.

### Species Cover Composition

This section will show each species' share of total Plot F outplant cover through time.

### Downloads

This section will point to Plot F processed datasets, summary tables, and figures after Plot F data are configured.

## Plot G

### Overview

Plot G now includes outplant match-file analyses for sections 0-0, 0-1, and 1-0, combined into one Plot G result. The supplied surveys span November 2025 through August 2026. Baseline survivorship starts at the first survey with present outplants in each section.

### Data Status

<details>
<summary>View source files and survey dates</summary>

The active Plot G files are:

```{r}
#| label: plot-g-configured-files

outplant_config %>%
  filter(plot == "Plot G") %>%
  select(plot, plot_section, month_start, month_end, month_start_date, month_end_date, file, plot_length_m, plot_width_m, taglab_area_units) %>%
  kable(
    col.names = c(
      "Plot", "Section", "Start month", "End month", "Start date", "End date", "File",
      "Plot length (m)", "Plot width (m)", "Area units"
    )
  )
```

</details>

### Depth Metadata

```{r}
#| label: plot-g-depth-summary

outplant_plot_depth_summary %>%
  filter(plot == "Plot G") %>%
  mutate(
    mean_depth_ft = round(mean_depth_ft, 1),
    min_depth_ft = round(min_depth_ft, 1),
    max_depth_ft = round(max_depth_ft, 1),
    depth_range_ft = round(depth_range_ft, 1),
    mean_depth_m = round(mean_depth_m, 2),
    min_depth_m = round(min_depth_m, 2),
    max_depth_m = round(max_depth_m, 2),
    depth_range_m = round(depth_range_m, 2)
  ) %>%
  select(
    plot,
    n_depth_markers,
    mean_depth_ft,
    min_depth_ft,
    max_depth_ft,
    depth_range_ft,
    mean_depth_m,
    min_depth_m,
    max_depth_m,
    depth_range_m
  ) %>%
  kable(
    col.names = c(
      "Plot", "Depth markers", "Mean depth (ft)", "Min depth (ft)",
      "Max depth (ft)", "Depth range (ft)", "Mean depth (m)",
      "Min depth (m)", "Max depth (m)", "Depth range (m)"
    )
  )
```

### QA/QC

<details>
<summary>View quality checks</summary>

```{r}
#| label: plot-g-file-audit

outplant_file_audit %>%
  filter(plot == "Plot G") %>%
  select(plot, plot_section, month_start, month_end, match_type, file, file_exists) %>%
  kable(
    col.names = c("Plot", "Section", "Start month", "End month", "Match type", "File", "File exists")
  )
```

```{r}
#| label: plot-g-interval-qa

outplant_interval_qa %>%
  filter(plot == "Plot G") %>%
  select(
    plot_section,
    month_start,
    month_end,
    n_rows,
    n_missing_genet,
    n_missing_species,
    n_negative_area_start,
    n_negative_area_end,
    actions,
    split_fuse_events
  ) %>%
  kable(
    col.names = c(
      "Section", "Start month", "End month", "Rows", "Missing Genet", "Missing species",
      "Negative start area", "Negative end area", "Actions", "Split/fuse events"
    )
  )
```

```{r}
#| label: plot-g-shared-month-continuity

outplant_shared_month_continuity_qa %>%
  filter(plot == "Plot G") %>%
  select(
    plot_section,
    shared_month,
    previous_end_n,
    next_start_n,
    in_both_snapshots,
    missing_from_next_start,
    new_in_next_start,
    species_mismatches,
    area_mismatches,
    max_abs_area_difference
  ) %>%
  mutate(max_abs_area_difference = round(max_abs_area_difference, 4)) %>%
  kable(
    col.names = c(
      "Section", "Shared month", "Previous file end n", "Next file start n",
      "In both", "Missing from next start", "New in next start",
      "Species mismatches", "Area mismatches", "Max area difference"
    )
  )
```

</details>

### Cumulative Survivorship

```{r}
#| label: plot-g-cumulative-survival-table

outplant_cumulative_survival_summary %>%
  filter(plot == "Plot G") %>%
  select(
    plot_section_label,
    month,
    baseline_month,
    n_baseline,
    n_died_interval,
    cumulative_deaths_observed,
    n_surviving_from_baseline,
    percent_cumulative_survival,
    percent_cumulative_survival_low,
    percent_cumulative_survival_high
  ) %>%
  mutate(
    percent_cumulative_survival = round(percent_cumulative_survival, 1),
    percent_cumulative_survival_low = round(percent_cumulative_survival_low, 1),
    percent_cumulative_survival_high = round(percent_cumulative_survival_high, 1)
  ) %>%
  kable(
    col.names = c(
      "Plot", "Month", "Baseline month", "Baseline n", "Deaths this interval",
      "Cumulative deaths", "Surviving from baseline",
      "Cumulative survival (%)", "95% CI low", "95% CI high"
    )
  )
```

```{r}
#| label: plot-g-cumulative-survival-plot
#| fig-width: 8
#| fig-height: 4.5
#| fig-alt: "Line plot of Plot G cumulative outplant survivorship over survey dates with confidence intervals and temperature overlay."

outplant_plot_short_cumulative_survival(
  outplant_cumulative_survival_summary %>% filter(plot == "Plot G")
)
```

### Interval Survivorship

```{r}
#| label: plot-g-interval-survival-table

outplant_survival_summary %>%
  filter(plot == "Plot G") %>%
  select(
    plot_section_label,
    interval_label,
    n_start,
    n_survived,
    n_died,
    n_born,
    percent_survival,
    percent_survival_low,
    percent_survival_high
  ) %>%
  mutate(
    percent_survival = round(percent_survival, 1),
    percent_survival_low = round(percent_survival_low, 1),
    percent_survival_high = round(percent_survival_high, 1)
  ) %>%
  kable(
    col.names = c(
      "Plot", "Interval", "Start n", "Survived n", "Died n", "Born n",
      "Interval survival (%)", "95% CI low", "95% CI high"
    )
  )
```

```{r}
#| label: plot-g-interval-survival-plot
#| fig-width: 8
#| fig-height: 4.5
#| fig-alt: "Line plot of Plot G interval survivorship between adjacent survey months with confidence intervals."

outplant_plot_short_interval_survival(
  outplant_survival_summary %>% filter(plot == "Plot G")
)
```

### Coral Cover

```{r}
#| label: plot-g-cover-table

outplant_cover_summary %>%
  filter(plot == "Plot G") %>%
  select(plot_section_label, month, n_outplants_present, total_outplant_area_m2, plot_area_m2, percent_outplant_cover) %>%
  mutate(
    total_outplant_area_m2 = round(total_outplant_area_m2, 6),
    percent_outplant_cover = round(percent_outplant_cover, 5)
  ) %>%
  kable(
    col.names = c(
      "Plot", "Month", "Outplants present", "Total outplant area (m2)",
      "Plot area (m2)", "Outplant cover (%)"
    )
  )
```

```{r}
#| label: plot-g-cover-plot
#| fig-width: 8
#| fig-height: 4.5
#| fig-alt: "Line plot of Plot G outplant cover through time as a percent of plot area."

outplant_plot_cover(
  outplant_cover_summary %>% filter(plot == "Plot G")
)
```

### Total Outplant Coral Cover Over Time

```{r}
#| label: plot-g-total-cover-bars
#| fig-width: 9
#| fig-height: 5.5
#| fig-alt: "Bar chart of summed outplant coral cover for Plot G by survey date, distinguishing complete and partial section coverage."

outplant_plot_total_cover_bars(
  outplant_cover_summary %>% filter(plot == "Plot G"),
  outplant_section_monthly_observations %>% filter(plot == "Plot G"),
  outplant_config %>% filter(plot == "Plot G")
)
```

### Species Prevalence

```{r}
#| label: plot-g-species-prevalence-table

outplant_species_prevalence_summary %>%
  filter(plot == "Plot G") %>%
  select(
    plot_section_label,
    month,
    species,
    n_outplants,
    percent_prevalence,
    total_outplant_area_m2,
    percent_cover_within_outplants
  ) %>%
  mutate(
    percent_prevalence = round(percent_prevalence, 1),
    total_outplant_area_m2 = round(total_outplant_area_m2, 6),
    percent_cover_within_outplants = round(percent_cover_within_outplants, 1)
  ) %>%
  kable(
    col.names = c(
      "Plot", "Month", "Species", "Outplant abundance", "Prevalence (%)",
      "Outplant area (m2)", "Share of outplant cover (%)"
    )
  )
```

```{r}
#| label: plot-g-species-prevalence-plot
#| fig-width: 8
#| fig-height: 4.5
#| fig-alt: "Stacked bar plot of Plot G outplant species prevalence by survey month."

outplant_plot_species_prevalence(
  outplant_species_prevalence_summary %>% filter(plot == "Plot G")
)
```

### Species Cover Composition

```{r}
#| label: plot-g-species-cover-plot
#| fig-width: 8
#| fig-height: 4.5
#| fig-alt: "Stacked bar plot of Plot G outplant cover composition by species and survey month."

outplant_plot_species_cover(
  outplant_species_prevalence_summary %>% filter(plot == "Plot G")
)
```

### Outplanted Coral Area by Species

```{r}
#| label: plot-g-species-area-plot
#| fig-width: 8
#| fig-height: 4.8
#| fig-alt: "Line chart of Plot G measured outplant area through time by species."

outplant_plot_species_area(
  outplant_species_area_summary %>% filter(plot == "Plot G")
)
```

### Growth Versus New or Lost Outplants

```{r}
#| label: plot-g-cover-change-source-plot
#| fig-width: 8
#| fig-height: 5
#| fig-alt: "Bar chart separating Plot G area change into growth or shrinkage, lost area, and newly observed outplants."

outplant_plot_cover_change_source(
  outplant_cover_change_source_summary %>% filter(plot == "Plot G")
)
```

### Downloads

Use the master tracking dataset and master summary dataset listed in the Home tab for Plot G results.

## Plot H

### Overview

Plot H combines the supplied TagLab sections into one plot-level result. Survey dates and section coverage are listed below; baseline survivorship starts at the first survey with present outplants in each section.

### Data Status

<details>
<summary>View source files and survey dates</summary>

The active Plot H files are:

```{r}
#| label: plot-h-configured-files

outplant_config %>%
  filter(plot == "Plot H") %>%
  select(plot, plot_section, month_start, month_end, month_start_date, month_end_date, file, plot_length_m, plot_width_m, taglab_area_units) %>%
  kable(
    col.names = c(
      "Plot", "Section", "Start month", "End month", "Start date", "End date", "File",
      "Plot length (m)", "Plot width (m)", "Area units"
    )
  )
```

</details>

### Depth Metadata

```{r}
#| label: plot-h-depth-summary

outplant_plot_depth_summary %>%
  filter(plot == "Plot H") %>%
  mutate(
    mean_depth_ft = round(mean_depth_ft, 1),
    min_depth_ft = round(min_depth_ft, 1),
    max_depth_ft = round(max_depth_ft, 1),
    depth_range_ft = round(depth_range_ft, 1),
    mean_depth_m = round(mean_depth_m, 2),
    min_depth_m = round(min_depth_m, 2),
    max_depth_m = round(max_depth_m, 2),
    depth_range_m = round(depth_range_m, 2)
  ) %>%
  select(
    plot,
    n_depth_markers,
    mean_depth_ft,
    min_depth_ft,
    max_depth_ft,
    depth_range_ft,
    mean_depth_m,
    min_depth_m,
    max_depth_m,
    depth_range_m
  ) %>%
  kable(
    col.names = c(
      "Plot", "Depth markers", "Mean depth (ft)", "Min depth (ft)",
      "Max depth (ft)", "Depth range (ft)", "Mean depth (m)",
      "Min depth (m)", "Max depth (m)", "Depth range (m)"
    )
  )
```

### QA/QC

<details>
<summary>View quality checks</summary>

```{r}
#| label: plot-h-file-audit

outplant_file_audit %>%
  filter(plot == "Plot H") %>%
  select(plot, plot_section, month_start, month_end, match_type, file, file_exists) %>%
  kable(
    col.names = c("Plot", "Section", "Start month", "End month", "Match type", "File", "File exists")
  )
```

```{r}
#| label: plot-h-interval-qa

outplant_interval_qa %>%
  filter(plot == "Plot H") %>%
  select(
    plot_section,
    month_start,
    month_end,
    n_rows,
    n_missing_genet,
    n_missing_species,
    n_negative_area_start,
    n_negative_area_end,
    actions,
    split_fuse_events
  ) %>%
  kable(
    col.names = c(
      "Section", "Start month", "End month", "Rows", "Missing Genet", "Missing species",
      "Negative start area", "Negative end area", "Actions", "Split/fuse events"
    )
  )
```

```{r}
#| label: plot-h-shared-month-continuity

outplant_shared_month_continuity_qa %>%
  filter(plot == "Plot H") %>%
  select(
    plot_section,
    shared_month,
    previous_end_n,
    next_start_n,
    in_both_snapshots,
    missing_from_next_start,
    new_in_next_start,
    species_mismatches,
    area_mismatches,
    max_abs_area_difference
  ) %>%
  mutate(max_abs_area_difference = round(max_abs_area_difference, 4)) %>%
  kable(
    col.names = c(
      "Section", "Shared month", "Previous file end n", "Next file start n",
      "In both", "Missing from next start", "New in next start",
      "Species mismatches", "Area mismatches", "Max area difference"
    )
  )
```

</details>

### Cumulative Survivorship

```{r}
#| label: plot-h-cumulative-survival-table

outplant_cumulative_survival_summary %>%
  filter(plot == "Plot H") %>%
  select(
    plot_section_label,
    month,
    baseline_month,
    n_baseline,
    n_died_interval,
    cumulative_deaths_observed,
    n_surviving_from_baseline,
    percent_cumulative_survival,
    percent_cumulative_survival_low,
    percent_cumulative_survival_high
  ) %>%
  mutate(
    percent_cumulative_survival = round(percent_cumulative_survival, 1),
    percent_cumulative_survival_low = round(percent_cumulative_survival_low, 1),
    percent_cumulative_survival_high = round(percent_cumulative_survival_high, 1)
  ) %>%
  kable(
    col.names = c(
      "Plot", "Month", "Baseline month", "Baseline n", "Deaths this interval",
      "Cumulative deaths", "Surviving from baseline",
      "Cumulative survival (%)", "95% CI low", "95% CI high"
    )
  )
```

```{r}
#| label: plot-h-cumulative-survival-plot
#| fig-width: 8
#| fig-height: 4.5
#| fig-alt: "Line plot of Plot H cumulative outplant survivorship over survey dates with confidence intervals and temperature overlay."

outplant_plot_cumulative_survival(
  outplant_cumulative_survival_summary %>% filter(plot == "Plot H"),
  outplant_daily_temperature_summary
)
```

### Interval Survivorship

```{r}
#| label: plot-h-interval-survival-table

outplant_survival_summary %>%
  filter(plot == "Plot H") %>%
  select(
    plot_section_label,
    interval_label,
    n_start,
    n_survived,
    n_died,
    n_born,
    percent_survival,
    percent_survival_low,
    percent_survival_high
  ) %>%
  mutate(
    percent_survival = round(percent_survival, 1),
    percent_survival_low = round(percent_survival_low, 1),
    percent_survival_high = round(percent_survival_high, 1)
  ) %>%
  kable(
    col.names = c(
      "Plot", "Interval", "Start n", "Survived n", "Died n", "Born n",
      "Interval survival (%)", "95% CI low", "95% CI high"
    )
  )
```

```{r}
#| label: plot-h-interval-survival-plot
#| fig-width: 8
#| fig-height: 4.5
#| fig-alt: "Line plot of Plot H interval survivorship between adjacent survey months with confidence intervals."

outplant_plot_interval_survival(
  outplant_survival_summary %>% filter(plot == "Plot H")
)
```

### Coral Cover

```{r}
#| label: plot-h-cover-table

outplant_cover_summary %>%
  filter(plot == "Plot H") %>%
  select(plot_section_label, month, n_outplants_present, total_outplant_area_m2, plot_area_m2, percent_outplant_cover) %>%
  mutate(
    total_outplant_area_m2 = round(total_outplant_area_m2, 6),
    percent_outplant_cover = round(percent_outplant_cover, 5)
  ) %>%
  kable(
    col.names = c(
      "Plot", "Month", "Outplants present", "Total outplant area (m2)",
      "Plot area (m2)", "Outplant cover (%)"
    )
  )
```

```{r}
#| label: plot-h-cover-plot
#| fig-width: 8
#| fig-height: 4.5
#| fig-alt: "Line plot of Plot H outplant cover through time as a percent of plot area."

outplant_plot_cover(
  outplant_cover_summary %>% filter(plot == "Plot H")
)
```

### Total Outplant Coral Cover Over Time

```{r}
#| label: plot-h-total-cover-bars
#| fig-width: 9
#| fig-height: 5.5
#| fig-alt: "Bar chart of summed outplant coral cover for Plot H by survey date, distinguishing complete and partial section coverage."

outplant_plot_total_cover_bars(
  outplant_cover_summary %>% filter(plot == "Plot H"),
  outplant_section_monthly_observations %>% filter(plot == "Plot H"),
  outplant_config %>% filter(plot == "Plot H")
)
```

### Species Prevalence

```{r}
#| label: plot-h-species-prevalence-table

outplant_species_prevalence_summary %>%
  filter(plot == "Plot H") %>%
  select(
    plot_section_label,
    month,
    species,
    n_outplants,
    percent_prevalence,
    total_outplant_area_m2,
    percent_cover_within_outplants
  ) %>%
  mutate(
    percent_prevalence = round(percent_prevalence, 1),
    total_outplant_area_m2 = round(total_outplant_area_m2, 6),
    percent_cover_within_outplants = round(percent_cover_within_outplants, 1)
  ) %>%
  kable(
    col.names = c(
      "Plot", "Month", "Species", "Outplant abundance", "Prevalence (%)",
      "Outplant area (m2)", "Share of outplant cover (%)"
    )
  )
```

```{r}
#| label: plot-h-species-prevalence-plot
#| fig-width: 8
#| fig-height: 4.5
#| fig-alt: "Stacked bar plot of Plot H outplant species prevalence by survey month."

outplant_plot_species_prevalence(
  outplant_species_prevalence_summary %>% filter(plot == "Plot H")
)
```

### Species Cover Composition

```{r}
#| label: plot-h-species-cover-plot
#| fig-width: 8
#| fig-height: 4.5
#| fig-alt: "Stacked bar plot of Plot H outplant cover composition by species and survey month."

outplant_plot_species_cover(
  outplant_species_prevalence_summary %>% filter(plot == "Plot H")
)
```

### Outplanted Coral Area by Species

```{r}
#| label: plot-h-species-area-plot
#| fig-width: 8
#| fig-height: 4.8
#| fig-alt: "Line chart of Plot H measured outplant area through time by species."

outplant_plot_species_area(
  outplant_species_area_summary %>% filter(plot == "Plot H")
)
```

### Growth Versus New or Lost Outplants

```{r}
#| label: plot-h-cover-change-source-plot
#| fig-width: 8
#| fig-height: 5
#| fig-alt: "Bar chart separating Plot H area change into growth or shrinkage, lost area, and newly observed outplants."

outplant_plot_cover_change_source(
  outplant_cover_change_source_summary %>% filter(plot == "Plot H")
)
```

### Downloads

Use the master tracking dataset and master summary dataset listed in the Home tab for Plot H results.
:::::::::::::::
