---
title: "DPNR Outplant Analyses"
page-layout: full
toc: false
---

```{r}
#| label: homepage-overview-data
#| include: false

# Rebuild from configured Matches so the homepage cannot use stale summaries
# when Quarto renders it before the detailed report.
source("R/03_outplant_interval_workflow.R")
home_latest <- outplant_cumulative_survival_summary |>
  dplyr::group_by(plot) |>
  dplyr::slice_max(survey_date, n = 1, with_ties = FALSE) |>
  dplyr::ungroup() |>
  dplyr::arrange(plot)
home_baseline_total <- sum(home_latest$n_baseline)
home_count <- function(x) format(x, big.mark = ",", scientific = FALSE, trim = TRUE)
```

<style>
#title-block-header {
  display: none;
}
</style>

<section class="site-hero" aria-labelledby="home-title">
<div class="site-hero__content">
<p class="site-kicker">Coral outplant monitoring</p>
<h1 id="home-title">DPNR Outplant Analyses</h1>
<p class="site-hero__lede">See how outplanted corals are surviving and growing across our monitoring plots.</p>
<div class="site-hero__actions" aria-label="Primary pages">
<a class="site-button site-button--primary" href="coral_survivorship_report.html">Open Analysis Report</a>
<a class="site-button site-button--secondary" href="all_coral_cover.html">View All Coral Cover</a>
</div>
<div class="site-hero__chips" aria-label="Current report scope">
<span>Plots A–E, G, H</span>
<span>82 match files</span>
<span>Updated September 23, 2026</span>
<span>Section coverage varies</span>
</div>
</div>
</section>

<section class="home-band home-band--metrics" aria-label="Outplant overview">
<div class="metric-strip">
<div class="metric-tile metric-tile--teal"><span>`r home_count(home_baseline_total)`</span><p>outplants tracked at baseline</p></div>
<div class="metric-tile metric-tile--coral"><span>`r nrow(home_latest)`</span><p>plots with monitoring data</p></div>
</div>
</section>

<section class="home-band" aria-label="Survivorship by plot">
<div class="home-section-heading">
<h2>How each plot is doing</h2>
<p>Survivorship is the percentage of baseline outplants still present at the latest survey with all configured sections represented.</p>
</div>

```{r}
#| label: homepage-plot-cards
#| echo: false
#| results: asis

cat('<div class="plot-overview-grid">')
for (i in seq_len(nrow(home_latest))) {
  plot_row <- home_latest[i, ]
  cat(sprintf(
    '<article class="plot-overview-card"><h3>%s</h3><p class="plot-overview-value">%.1f%%<span>survivorship</span></p><p><strong>%s</strong> of <strong>%s</strong> baseline outplants remain.</p><p class="plot-overview-date">Survey: %s</p></article>',
    plot_row$plot, plot_row$percent_cumulative_survival,
    home_count(plot_row$n_surviving_from_baseline), home_count(plot_row$n_baseline),
    format(as.Date(plot_row$survey_date), "%d %b %Y")
  ))
}
cat('</div>')
```

<p class="overview-note">Counts represent tracked Genets in the Matches data, not every fragment ever planted or later additions. Survey dates differ between plots. Plot E uses January 2026 because later surveys cover only part of the plot. Plot F has no supplied monitoring data. <a href="coral_survivorship_report.html">See the report for data-quality flags and full results.</a></p>
</section>

<section class="home-band home-band--intro" aria-label="Project overview">
<div class="home-grid home-grid--two">
<article class="home-feature">
<i class="bi bi-graph-up-arrow home-feature__icon" aria-hidden="true"></i>
<p class="home-feature__label">Start here</p>
<h2>Analysis Report</h2>
<p>Presentation-ready survivorship, interval survival, cover, species prevalence, QA/QC, and plot-specific tabs.</p>
<a href="coral_survivorship_report.html">Go to report</a>
</article>
<article class="home-feature">
<i class="bi bi-grid-3x3-gap home-feature__icon" aria-hidden="true"></i>
<p class="home-feature__label">Whole plot</p>
<h2>All Coral Cover</h2>
<p>Coral-cover summaries for all annotations across configured plot surveys, separate from the outplant-only workflow.</p>
<a href="all_coral_cover.html">Review cover</a>
</article>
</div>
</section>

<section class="home-band home-band--reef" aria-label="Analysis highlights">
<div class="home-section-heading">
<p class="site-kicker">What this site tracks</p>
<h2>A cleaner view of survivorship, cover, and species change</h2>
</div>
<div class="reef-grid">
<article class="reef-card reef-card--survival">
<span>Survival</span>
<h3>Cumulative and interval survivorship</h3>
<p>Baseline survival curves and month-to-month diagnostic checks stay side by side.</p>
</article>
<article class="reef-card reef-card--cover">
<span>Cover</span>
<h3>Outplant and whole-plot cover</h3>
<p>Small outplant cover signals and all-coral plot cover are separated so each stays interpretable.</p>
</article>
<article class="reef-card reef-card--qa">
<span>QA/QC</span>
<h3>File checks before interpretation</h3>
<p>Configured files, shared-month continuity, Genet identity, and missing values remain visible.</p>
</article>
</div>
</section>

<section class="home-band" aria-label="Update workflow">
<div class="home-section-heading">
<p class="site-kicker">Update flow</p>
<h2>From TagLab exports to GitHub Pages</h2>
</div>
<ol class="workflow-list">
<li><span>01</span><p>Edit plot config rows under <code>config/outplant_interval_files/</code> or <code>config/all_coral_survey_files/</code>.</p></li>
<li><span>02</span><p>Render the Quarto website so processed data, output tables, figures, and <code>docs/</code> are rebuilt together.</p></li>
<li><span>03</span><p>Review file-audit and QA/QC tables before interpreting the plots or publishing the update.</p></li>
<li><span>04</span><p>Run <code>Rscript scripts/pre_push_check.R</code>, then commit and push source, outputs, and rendered site files.</p></li>
</ol>
</section>

<section class="home-band home-band--outputs" aria-label="Recommended outputs">
<div class="home-section-heading">
<p class="site-kicker">Recommended outputs</p>
<h2>Open these first</h2>
</div>
<div class="output-strip">
<code>data_processed/outplant_master_tracking_dataset.csv</code>
<code>outputs/Tables/outplant_master_summary_dataset.csv</code>
</div>
</section>
