---
title: "Interactive Coki Map"
page-layout: full
toc: true
---

```{r}
#| label: map-setup
#| include: false

source(file.path("R", "05_interactive_coki_map.R"))
```

## Coki A–H

Zoom in to inspect the GPS-defined boundaries. Click a Coki polygon for its latest outplant count, species composition, observed outplant area, percent cover, and cumulative survivorship. Corner markers can be shown or hidden from the layer control.

```{r}
#| label: coki-interactive-map
#| echo: false
#| fig-width: 14
#| fig-height: 9

coki_interactive_map
```

The default satellite layer provides the clearest view of the reef setting. The street-map layer is available as a lighter alternative. Polygon boundaries connect markers M1, M2, M3, and M4 in the field-layout order provided with the coordinates.

### How the popup numbers are calculated

- **Outplants present and species counts** use the latest available TagLab snapshot for that Coki.
- **Observed outplant area** is the summed planar area of those present outplants.
- **Outplant cover** divides observed outplant area by the confirmed 480 m² Coki area.
- **Cumulative survivorship** uses the latest survey with complete configured-section coverage. This can be earlier than the cover snapshot when later monitoring is partial.
- Coki F has coordinates but no configured outplant monitoring files, so its popup reports that data are unavailable.

The map uses field GPS coordinates as supplied. Consumer GPS uncertainty and underwater marker placement mean the polygons are monitoring boundaries, not legal survey boundaries.
